---
title: "activity level analysis"
output: html_notebook
---


```{r}
library(ggplot2)
library(dplyr)
```

```{r}
source("util.R")
```

analyze activity levels of students
  for each time period (2 days -> period 1 - 7)
    calculate number of activities to this point (all previous activities for this task (period <= x))
    generate ranking of students
      1 (most active), 2 (medium active), 3 (least active)
  
aim: table with students that contains the activity level for each perdiod in one column

then: analyze transitions between levels
expectation:  levels stay the same for Ko
              levels increase for M/MG in the end
              
### TASK1 ###
#############
## all activities for task1
```{r}
## all activity sequences
sequences_task1 <- read.csv2("/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/t1_t2_t3_activities_with_start.csv", stringsAsFactors = F) %>% subset(select=-c(X, class)) %>% 
  addTask() %>% 
  
###!!!### filter which task
  filter(task == "task1") %>% 
###!!!### filter type (forum / wiki)
  #filter(type == "wiki") %>% 
  filter(!user_id == "start" )
```

```{r}
# filter sub-sequences to only contain relevant activities (timewise)
# period 1: day 1,2
# period 2: day 3,4
# ...

seq_task1_period1 <- sequences_task1 %>% 
  filter(period <= 2)
seq_task1_period2 <- sequences_task1 %>% 
  filter(period <= 4)
seq_task1_period3 <- sequences_task1 %>% 
  filter(period <= 6)
seq_task1_period4 <- sequences_task1 %>% 
  filter(period <= 8)
seq_task1_period5 <- sequences_task1 %>% 
  filter(period <= 10)
seq_task1_period6 <- sequences_task1 %>% 
  filter(period <= 12)
seq_task1_period7 <- sequences_task1 %>% 
  filter(period <= 14)

```

```{r}
activity_counts_task1_period1 <- calculateUserActivityCount(seq_task1_period1) %>% 
  addActivityRank2() %>%
  normalizeRank() %>% 
  addConditions()
activity_counts_task1_period2 <- calculateUserActivityCount(seq_task1_period2) %>% 
  addActivityRank2() %>%
  normalizeRank() %>%
  addConditions()
activity_counts_task1_period3 <- calculateUserActivityCount(seq_task1_period3) %>% 
  addActivityRank2() %>%
  normalizeRank() %>% 
  addConditions()
activity_counts_task1_period4 <- calculateUserActivityCount(seq_task1_period4) %>% 
  addActivityRank2() %>%
  normalizeRank() %>% 
  addConditions()
activity_counts_task1_period5 <- calculateUserActivityCount(seq_task1_period5) %>% 
  addActivityRank2() %>%
  normalizeRank() %>% 
  addConditions()
activity_counts_task1_period6 <- calculateUserActivityCount(seq_task1_period6) %>% 
  addActivityRank2() %>%
  normalizeRank() %>% 
  addConditions()
activity_counts_task1_period7 <- calculateUserActivityCount(seq_task1_period7) %>% 
  addActivityRank2() %>%
  normalizeRank() %>% 
  addConditions()

# start with day 2 if there were no activities on day one
task1_changing_user_activity_count <- activity_counts_task1_period1
task1_changing_user_activity_count$period = 1

task1_changing_user_activity_count <- addValues(task1_changing_user_activity_count, activity_counts_task1_period2, 2)
task1_changing_user_activity_count <- addValues(task1_changing_user_activity_count, activity_counts_task1_period3, 3)
task1_changing_user_activity_count <- addValues(task1_changing_user_activity_count, activity_counts_task1_period4, 4)
task1_changing_user_activity_count <- addValues(task1_changing_user_activity_count, activity_counts_task1_period5, 5)
task1_changing_user_activity_count <- addValues(task1_changing_user_activity_count, activity_counts_task1_period6, 6)
task1_changing_user_activity_count <- addValues(task1_changing_user_activity_count, activity_counts_task1_period7, 7)


# replace NaN values
task1_changing_user_activity_count$norm_rank[is.nan(task1_changing_user_activity_count$norm_rank)] <- 0

```

```{r}
#task1_changing_user_activity_count <- task1_changing_user_activity_count
# write.csv2(task1_changing_user_activity_count, "/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/task1_per_1_7_changing_activity_count.csv", row.names = F)
```

### TASK2 ###
#############
## all activities for task1
```{r}
## all activity sequences
sequences_task2 <- read.csv2("/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/t1_t2_t3_activities_with_start.csv", stringsAsFactors = F) %>% subset(select=-c(X, class)) %>% 
  addTask() %>% 
  
###!!!### filter which task
  filter(task == "task2") %>% 
###!!!### filter type (forum / wiki)
  #filter(type == "wiki") %>% 
  filter(!user_id == "start" )
```

```{r}
# filter sub-sequences to only contain relevant activities (timewise)
# period 1: day 1,2
# period 2: day 3,4
# ...

seq_task2_period1 <- sequences_task2 %>% 
  filter(period <= 2)
seq_task2_period2 <- sequences_task2 %>% 
  filter(period <= 4)
seq_task2_period3 <- sequences_task2 %>% 
  filter(period <= 6)
seq_task2_period4 <- sequences_task2 %>% 
  filter(period <= 8)
seq_task2_period5 <- sequences_task2 %>% 
  filter(period <= 10)
seq_task2_period6 <- sequences_task2 %>% 
  filter(period <= 12)
seq_task2_period7 <- sequences_task2 %>% 
  filter(period <= 14)

```

```{r}
activity_counts_task2_period1 <- calculateUserActivityCount(seq_task2_period1) %>% 
  addActivityRank2() %>%
  normalizeRank() %>% 
  addConditions()
activity_counts_task2_period2 <- calculateUserActivityCount(seq_task2_period2) %>% 
  addActivityRank2() %>%
  normalizeRank() %>% 
  addConditions()
activity_counts_task2_period3 <- calculateUserActivityCount(seq_task2_period3) %>% 
  addActivityRank2() %>%
  normalizeRank() %>%
  addConditions()
activity_counts_task2_period4 <- calculateUserActivityCount(seq_task2_period4) %>% 
  addActivityRank2() %>%
  normalizeRank() %>%
  addConditions()
activity_counts_task2_period5 <- calculateUserActivityCount(seq_task2_period5) %>% 
  addActivityRank2() %>%
  normalizeRank() %>%
  addConditions()
activity_counts_task2_period6 <- calculateUserActivityCount(seq_task2_period6) %>% 
  addActivityRank2() %>%
  normalizeRank() %>%
  addConditions()
activity_counts_task2_period7 <- calculateUserActivityCount(seq_task2_period7) %>% 
  addActivityRank2() %>%
  normalizeRank() %>%
  addConditions()

# start with day 2 if there were no activities on day one
task2_changing_user_activity_count <- activity_counts_task2_period1
task2_changing_user_activity_count$period = 1

task2_changing_user_activity_count <- addValues(task2_changing_user_activity_count, activity_counts_task2_period2, 2)
task2_changing_user_activity_count <- addValues(task2_changing_user_activity_count, activity_counts_task2_period3, 3)
task2_changing_user_activity_count <- addValues(task2_changing_user_activity_count, activity_counts_task2_period4, 4)
task2_changing_user_activity_count <- addValues(task2_changing_user_activity_count, activity_counts_task2_period5, 5)
task2_changing_user_activity_count <- addValues(task2_changing_user_activity_count, activity_counts_task2_period6, 6)
task2_changing_user_activity_count <- addValues(task2_changing_user_activity_count, activity_counts_task2_period7, 7)

# replace NaN values
task2_changing_user_activity_count$norm_rank[is.nan(task2_changing_user_activity_count$norm_rank)] <- 0

```

```{r}
# task2_changing_user_activity_count <- task2_changing_user_activity_count
# write.csv2(task2_changing_user_activity_count, "/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/task2_per_1_7_changing_activity_count.csv", row.names = F)
```

### TASK3 ###
#############
## all activities for task1
```{r}
## all activity sequences
sequences_task3 <- read.csv2("/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/t1_t2_t3_activities_with_start.csv", stringsAsFactors = F) %>% subset(select=-c(X, class)) %>% 
  addTask() %>% 
  
###!!!### filter which task
  filter(task == "task3") %>% 
###!!!### filter type (forum / wiki)
  #filter(type == "wiki") %>% 
  filter(!user_id == "start" )
```

```{r}
# filter sub-sequences to only contain relevant activities (timewise)
# period 1: day 1,2
# period 2: day 3,4
# ...

seq_task3_period1 <- sequences_task3 %>% 
  filter(period <= 2)
seq_task3_period2 <- sequences_task3 %>% 
  filter(period <= 4)
seq_task3_period3 <- sequences_task3 %>% 
  filter(period <= 6)
seq_task3_period4 <- sequences_task3 %>% 
  filter(period <= 8)
seq_task3_period5 <- sequences_task3 %>% 
  filter(period <= 10)
seq_task3_period6 <- sequences_task3 %>% 
  filter(period <= 12)
seq_task3_period7 <- sequences_task3 %>% 
  filter(period <= 14)

```

```{r}
activity_counts_task3_period1 <- calculateUserActivityCount(seq_task3_period1) %>% 
  addActivityRank2() %>%
  normalizeRank() %>%
  addConditions()
activity_counts_task3_period2 <- calculateUserActivityCount(seq_task3_period2) %>% 
  addActivityRank2() %>%
  normalizeRank() %>%
  addConditions()
activity_counts_task3_period3 <- calculateUserActivityCount(seq_task3_period3) %>% 
  addActivityRank2() %>%
  normalizeRank() %>%
  addConditions()
activity_counts_task3_period4 <- calculateUserActivityCount(seq_task3_period4) %>% 
  addActivityRank2() %>%
  normalizeRank() %>%
  addConditions()
activity_counts_task3_period5 <- calculateUserActivityCount(seq_task3_period5) %>% 
  addActivityRank2() %>%
  normalizeRank() %>%
  addConditions()
activity_counts_task3_period6 <- calculateUserActivityCount(seq_task3_period6) %>% 
  addActivityRank2() %>%
  normalizeRank() %>%
  addConditions()
activity_counts_task3_period7 <- calculateUserActivityCount(seq_task3_period7) %>% 
  addActivityRank2() %>%
  normalizeRank() %>%
  addConditions()

# start with day 2 if there were no activities on day one
task3_changing_user_activity_count <- activity_counts_task3_period1
task3_changing_user_activity_count$period = 1

task3_changing_user_activity_count <- addValues(task3_changing_user_activity_count, activity_counts_task3_period2, 2)
task3_changing_user_activity_count <- addValues(task3_changing_user_activity_count, activity_counts_task3_period3, 3)
task3_changing_user_activity_count <- addValues(task3_changing_user_activity_count, activity_counts_task3_period4, 4)
task3_changing_user_activity_count <- addValues(task3_changing_user_activity_count, activity_counts_task3_period5, 5)
task3_changing_user_activity_count <- addValues(task3_changing_user_activity_count, activity_counts_task3_period6, 6)
task3_changing_user_activity_count <- addValues(task3_changing_user_activity_count, activity_counts_task3_period7, 7)

# replace NaN values
task3_changing_user_activity_count$norm_rank[is.nan(task3_changing_user_activity_count$norm_rank)] <- 0

```

```{r}
# task3_changing_user_activity_count <- task3_changing_user_activity_count
# write.csv2(task3_changing_user_activity_count, "/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/task3_per_1_7_changing_activity_count.csv", row.names = F)
```



### READ PREPARED DATA ###
```{r}
task1_changing_user_activity_count <- read.csv2("/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/task1_per_1_7_changing_activity_count.csv") %>% 
  arrange(activity_count)

task2_changing_user_activity_count <- read.csv2("/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/task2_per_1_7_changing_activity_count.csv") %>% 
  arrange(activity_count)

task3_changing_user_activity_count <- read.csv2("/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/task3_per_1_7_changing_activity_count.csv") %>% 
  arrange(activity_count)
```

```{r}
View(task1_changing_user_activity_count)
View(t1_test)
View(activity_counts_task3_period7)
```


### for overall ranks (not normalized)
### compare each period to the previous period
### add variable which states changes in the ranking

```{r}
# Task1
t1_test <- task1_changing_user_activity_count %>% 
  group_by(user_id) %>% 
  arrange(period, .by_group = T) %>% 
  mutate(ranking_change = -(rank -lag(rank)))

t1_test_2 <- t1_test %>% 
  filter(!is.na(ranking_change)) %>% 
  filter(!ranking_change == 0) %>% 
  group_by(condition) %>% 
  summarise(average_rank_change1 = mean(ranking_change))
  #summarise(accum_rank_change = sum(ranking_change))

# Task2
t2_test <- task2_changing_user_activity_count %>% 
  group_by(user_id) %>% 
  arrange(period, .by_group = T) %>% 
  mutate(ranking_change = -(rank -lag(rank)))

t2_test_2 <- t2_test %>% 
  filter(!is.na(ranking_change)) %>% 
  filter(!ranking_change == 0) %>% 
  group_by(condition) %>% 
  summarise(average_rank_change2 = mean(ranking_change))

# Task3
t3_test <- task3_changing_user_activity_count %>% 
  group_by(user_id) %>% 
  arrange(period, .by_group = T) %>% 
  mutate(ranking_change = -(rank -lag(rank)))

t3_test_2 <- t3_test %>% 
  filter(!is.na(ranking_change)) %>% 
  #filter(!ranking_change == 0) %>% 
  group_by(condition) %>% 
  summarise(average_rank_change3 = mean(ranking_change))

change_merge <- merge(t1_test_2, t2_test_2) %>% 
  merge(t3_test_2)
```

### for normalized ranks 
### compare each period to the previous period
### add variable which states changes in the ranking
# 0: best rank
# 1: worst rank
# -> for change: the lower the better 

```{r}

# task 1
t1_norm_test <- task1_changing_user_activity_count %>% 
  group_by(user_id) %>% 
  arrange(period, .by_group = T) %>% 
  mutate(ranking_change = (norm_rank -lag(norm_rank)))

t1_norm_test_2 <- t1_norm_test %>% 
  filter(!is.na(ranking_change)) %>% 
  #filter(!ranking_change == 0) %>% 
  group_by(condition) %>% 
  summarise(average_rank_change1 = mean(ranking_change))
  #summarise(accum_rank_change = sum(ranking_change))

# task 2 
t2_norm_test <- task2_changing_user_activity_count %>% 
  group_by(user_id) %>% 
  arrange(period, .by_group = T) %>% 
  mutate(ranking_change = (norm_rank -lag(norm_rank)))

t2_norm_test_2 <- t2_norm_test %>% 
  filter(!is.na(ranking_change)) %>% 
  #filter(!ranking_change == 0) %>% 
  group_by(condition) %>% 
  summarise(average_rank_change2 = mean(ranking_change))
  #summarise(accum_rank_change = sum(ranking_change))

# task 3

t3_norm_test <- task3_changing_user_activity_count %>% 
  group_by(user_id) %>% 
  arrange(period, .by_group = T) %>% 
  mutate(ranking_change = (norm_rank -lag(norm_rank)))

t3_norm_test_2 <- t3_norm_test %>% 
  filter(!is.na(ranking_change)) %>% 
  #filter(!ranking_change == 0) %>% 
  group_by(condition) %>% 
  summarise(average_rank_change3 = mean(ranking_change))
  #summarise(accum_rank_change = sum(ranking_change))

norm_change_merge <- merge(t1_norm_test_2, t2_norm_test_2) %>% 
  merge(t3_norm_test_2)
```








