---
title: "CVK Kurs WS 19/20 - SozPsy Analyse"
output: html_notebook
---

## INSTALL LIBRARIES (ONCE)
```{r}
# install.packages("dplyr")
```



## LOAD NECESSARY LIBRARYS
```{r}
library(dplyr)
library(reldist)
```

## SOME USEFUL FUNCTIONS
```{r}
# writing data frame to csv file
# write.csv2(<data table name>, "<path/filename.csv>")
# write.csv2(all_sequences, "/home/doberstein/Desktop/all_sequences.csv", row.names = F)

# reading data from csv file into R data frame
# <data frame name> <- read.csv2("<path/filename.csv", stringsAsFactors = F)
# all_groups_and_users <- read.csv2("/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/t1_t2_t3_activities_with_start.csv", stringsAsFactors = F)

```

##UTIL
```{r}
# function to add conditions to dataset based on group_id
addConditionsCVK2 <- function(df) {
  if (nrow(df) > 0) {
    df$condition <- NA
    
    # Task1:
    # M_H:    493 - 498 (mit Heraushebung)
    # M_H_T:  500 - 505 (mit Heraushebung, transparenz)
    # O_H:    486 - 491 (ohne Heraushebung)
    
    # Task2:
    # M_H:    521 - 525 (mit Heraushebung)
    # M_H_T:  526 - 531 (mit Heraushebung, transparenz)
    # O_H:    514 - 519 (ohne Heraushebung)
    
    # Task3:
    # S:      536 - 543 (System)
    # S_R:    544 - 549 (System + Reflexion)
    
    # Task4:
    # M:      553 - 559 (Mensch)
    # SY:     560 - 565 (System)     
    
    
    # Task1
    df$condition[df$group_id %in% c(493:498)] <- "M_H"
    df$condition[df$group_id %in% c(500:505)] <- "M_H_T"
    df$condition[df$group_id %in% c(486:491)] <- "O_H"
    
    # Task2
    df$condition[df$group_id %in% c(521:525)] <- "M_H"
    df$condition[df$group_id %in% c(526:531)] <- "M_H_T"
    df$condition[df$group_id %in% c(514:519)] <- "O_H"
    
    # Task3
    df$condition[df$group_id %in% c(536:543)] <- "S"
    df$condition[df$group_id %in% c(544:549)] <- "S_R"
    
    # Task4
    df$condition[df$group_id %in% c(553:559)] <- "M"
    df$condition[df$group_id %in% c(560:565)] <- "SY"
    
  }
  
  df
}

addTaskCVK2 <- function(df) {
  if (nrow(df) > 0) {
    df$task <- NA
    
    # Task1
    df$task[df$group_id %in% c(486:505)] <- "task1"
    
    # Task2
    df$task[df$group_id %in% c(514:531)] <- "task2"
    
    # Task3
    df$task[df$group_id %in% c(536:549)] <- "task3"
    
    # Task4
    df$task[df$group_id %in% c(553:565)] <- "task4"
  }
  
  df
}
```


## LOAD DATASET
### Dataset contains all relevant activities (forum posts / wiki updates) for grouptasks 1,2 for the conditions:
# Task1:
# M_H:    493 - 498 (mit Heraushebung)
# M_H_T:  500 - 505 (mit Heraushebung, transparenz)
# O_H:    486 - 491 (ohne Heraushebung)

# Task2:
# M_H:    521 - 525 (mit Heraushebung)
# M_H_T:  526 - 531 (mit Heraushebung, transparenz)
# O_H:    514 - 519 (ohne Heraushebung)

### (Groups for "Keine Rückmeldung" were omitted from the dataset)
### For each group a "start" activity has been added to the "activity sequence" so that the startpoint for the task is apparent (e.g. to find initial inactivity)
```{r}
all_sequences_t1 <- read.csv2("/home/doberstein/Dropbox/D/uni/IKARion/CVK 2_0/analysis/t1_activities_with_start.csv", stringsAsFactors = F) %>% subset(select=-class)
all_sequences_t2 <- read.csv2("/home/doberstein/Dropbox/D/uni/IKARion/CVK 2_0/analysis/t2_activities_with_start.csv", stringsAsFactors = F) %>% subset(select=-class)

all_sequences <- bind_rows(all_sequences_t1, all_sequences_t2)


# columns: 
# names(all_sequences)

# "group_id"    : group id (int)
# "content"     : text content of the activity. complete message for forum activities, complete wiki revision for wiki activities
# "object_id"   :
# "object_name" :
# "object_type" :
# "timestamp"   : unix timestamp stating the time that the activity occured
# "user_id"     : user id (anonymized)
# "verb_id"     :
# "wordcount"   : number of words for forum activities, difference between number of words in current and last revision for wiki articles
# "condition"   : Ko: Kontrollgruppe; M: Mirroring; MG: Mirroring&Guiding
# "day"         : day that the activity occured
# "period"      : relative day that the activity occured counted from the task beginning (1-14 for all tasks)
# "type"        : wiki / forum



# read data containing all users with groups and condition (Groups for "Keine Rückmeldung" are omitted)
all_groups_and_users_t1 <- read.csv2("/home/doberstein/Dropbox/D/uni/IKARion/CVK 2_0/analysis/task1_groups_and_users.csv", stringsAsFactors = F) %>% 
  subset(select = -X)

all_groups_and_users_t2 <- read.csv2("/home/doberstein/Dropbox/D/uni/IKARion/CVK 2_0/analysis/task2_groups_and_users.csv", stringsAsFactors = F) %>% 
  subset(select = -X)

all_groups_and_users <- bind_rows(all_groups_and_users_t1, all_groups_and_users_t2)
```

### GET ACTIVITY DATA FOR ONE GROUP
```{r}
group_487 <- all_sequences %>% 
  filter(group_id == 487)

group_487

# write as csv
#write.csv2(group_487, "/home/doberstein/Desktop/group_487.csv", row.names = F)
```

### FILTER OUT START ACTIVITY
```{r}
one_group <- all_sequences %>% 
  filter(group_id == 487) %>% 
  filter(!user_id == "start") 
```

### ACTIVITY COUNT PER USER PER GROUP
```{r}
activity_count_for_active_users <- all_sequences %>% 
  filter(!user_id == "start") %>% 
  group_by(group_id, user_id) %>% 
  summarise(activity_count = n())

activity_count_for_active_users
```
### ADDING INACTIVE USERS
```{r}
# file with all groups and users, set activity_count to 0
add_groups_and_users <- all_groups_and_users %>%
    select(c(group_id, user_id)) %>% 
    mutate(activity_count = 0)

# all inactive users 
missing <- anti_join(add_groups_and_users, activity_count_for_active_users, by = c("group_id", "user_id"))

activity_count_for_all_users <- full_join(missing, activity_count_for_active_users)

activity_count_for_all_users
```

# IKARion Logfiles zu Wordcount in Forum und Wiki

### WORDCOUNT FOR EACH USER
```{r}
wordcount_for_active_users <- all_sequences %>% 
  filter(!user_id == "start") %>% 
  # filter(period <= 3) %>%  filter out activities after day 3
  # filter(period <= 7) %>%  filter out activities after day 3
  # filter(period <= 10) %>%  filter out activities after day 3
  # filter(period <= 12) %>%  filter out activities after day 3
  # filter(period <= 14) %>%  filter out activities after day 3
  group_by(group_id, user_id) %>% 
  summarise(overall_wordcount = sum(wordcount))

# file with all groups and users, set activity_count to 0
add_groups_and_users <- all_groups_and_users %>%
    select(c(group_id, user_id)) %>% 
    mutate(overall_wordcount = 0)

# all inactive users 
missing <- anti_join(add_groups_and_users, wordcount_for_active_users, by = c("group_id", "user_id"))

wordcount_for_all_users <- full_join(missing, wordcount_for_active_users)

wordcount_for_all_users <- addConditionsCVK2(wordcount_for_all_users)
```

## FORUM WORDCOUNT FOR EACH USER
```{r}
forum_wordcount_for_active_users <- all_sequences %>% 
  filter(!user_id == "start") %>% 
  filter(type == "forum") %>% 
  group_by(group_id, user_id) %>% 
  summarise(forum_wordcount = sum(wordcount))

# file with all groups and users, set activity_count to 0
add_groups_and_users <- all_groups_and_users %>%
    select(c(group_id, user_id)) %>% 
    mutate(forum_wordcount = 0)

# all inactive users 
missing <- anti_join(add_groups_and_users, forum_wordcount_for_active_users, by = c("group_id", "user_id"))

forum_wordcount_for_all_users <- full_join(missing, forum_wordcount_for_active_users) %>% 
  addConditionsCVK2()

```

## WIKI WORDCOUNT FOR EACH USER
```{r}
wiki_wordcount_for_active_users <- all_sequences %>% 
  filter(!user_id == "start") %>% 
  filter(type == "wiki") %>% 
  group_by(group_id, user_id) %>% 
  summarise(wiki_wordcount = sum(wordcount))

# file with all groups and users, set activity_count to 0
add_groups_and_users <- all_groups_and_users %>%
    select(c(group_id, user_id)) %>% 
    mutate(wiki_wordcount = 0)

# all inactive users 
missing <- anti_join(add_groups_and_users, wiki_wordcount_for_active_users, by = c("group_id", "user_id"))

wiki_wordcount_for_all_users <- full_join(missing, wiki_wordcount_for_active_users) %>% 
  addConditionsCVK2()
```

## WORDCOUNT FOR EACH USER AFTER 7 DAYS
```{r}
wordcount_for_active_users_7d <- all_sequences %>% 
  filter(!user_id == "start") %>% 
  filter(period <= 7) %>% # filter out activities that occured after day 7
  group_by(group_id, user_id) %>% 
  summarise(overall_wordcount_7d = sum(wordcount))

# file with all groups and users, set activity_count to 0
add_groups_and_users <- all_groups_and_users %>%
    select(c(group_id, user_id)) %>% 
    mutate(overall_wordcount_7d = 0)

# all inactive users 
missing <- anti_join(add_groups_and_users, wordcount_for_active_users_7d, by = c("group_id", "user_id"))

wordcount_for_all_users_7d <- full_join(missing, wordcount_for_active_users_7d) %>% 
  addConditionsCVK2()

wordcount_for_all_users_7d
```

## MERGING DATAFRAMES
```{r}
wordcount_for_all_users
forum_wordcount_for_all_users
wiki_wordcount_for_all_users
wordcount_for_all_users_7d

complete_wordcount_data <- merge(wordcount_for_all_users, forum_wordcount_for_all_users) %>% 
  merge(wiki_wordcount_for_all_users) %>% 
  merge(wordcount_for_all_users_7d)
  


```

#IKARion Zeitabstand zwischen Forenbeiträgen

## TIME BETWEEN FORUM POSTS
```{r}
forum_latency <- all_sequences %>% 
  filter(type == "forum" | type == "start") %>% 
  group_by(group_id) %>% 
  mutate(forum_latency_sec = timestamp - lag(timestamp)) %>% 
  addConditionsCVK2()
```

## AVERAGE TIME BETWEEN FORUM POSTS BY GROUP
```{r}
forum_latency_by_group <- forum_latency %>% 
  filter(!user_id == "start") %>% 
  group_by(group_id) %>% 
  summarise(average_latency = mean(forum_latency_sec))

forum_activity_count_by_group <- forum_latency %>% 
  filter(!user_id == "start") %>% 
  group_by(group_id) %>% 
  summarise(forum_activity_count = n())

forum_data <- merge(forum_latency_by_group, forum_activity_count_by_group) %>% 
  addConditionsCVK2()

```


## TIME BETWEEN WIKI UPDATES
```{r}
wiki_latency <- all_sequences %>% 
  filter(type == "wiki" | type == "start") %>% 
  group_by(group_id) %>% 
  mutate(wiki_latency_sec = timestamp - lag(timestamp))
```

## TIME BETWEEN ANY KIND OF ACTIVITY
```{r}
activity_latency <- all_sequences %>% 
  group_by(group_id) %>% 
  mutate(activity_latency_sec = timestamp - lag(timestamp))

## maximal period of inactivity over all groups (in days)
max(activity_latency$activity_latency_sec, na.rm = T) / 60 / 60 / 24

```

## Aktivitäten für Themenblock 1
### Task1: Integrationsmodelle 
### GruppenIDs: 154 - 174
```{r}
# all task 1 activities
task1_activities <- all_sequences %>% 
  filter(group_id %in% c(486:505)) %>% 
  filter(!user_id == "start")

# all task 1 forum activities
task1_forum_activities <- task1_activities %>% 
  filter(type == "forum")

# all task 1 wiki activities
task1_wiki_activities <- task1_activities %>% 
  filter(type == "wiki")

# all task 1 activities for condition "Kontrollgruppe"
task1_activities_M_H <- task1_activities %>% 
  filter(condition == "M_H")

# all task 1 activities for one group (154)
task1_activities_487 <- task1_activities %>% 
  filter(group_id == 487)
```


# IKARion Logfiles zu Gini-Koeffizient in Forum und Wiki
```{r}
# gini calculation for all activities (forum + wiki combined) for complete task (14 days)

# (already done above, see calculation for variable: "wordcount_for_all_users")
gini_coeff_overall <- wordcount_for_all_users %>% 
  group_by(group_id) %>% 
  summarize(gini_overall = gini(overall_wordcount)*length(overall_wordcount)/(length(overall_wordcount)-1))

```

### WORDCOUNTS AND GINI AFTER DAY 3
```{r}
# wordcounts after day 3
wordcount_for_active_users_3d <- all_sequences %>% 
  filter(!user_id == "start") %>% 
  filter(period <= 3) %>% 
  group_by(group_id, user_id) %>% 
  summarise(wordcount_3d = sum(wordcount))

# file with all groups and users, set activity_count to 0
add_groups_and_users <- all_groups_and_users %>%
    select(c(group_id, user_id)) %>% 
    mutate(wordcount_3d = 0)

# all inactive users 
missing <- anti_join(add_groups_and_users, wordcount_for_active_users_3d, by = c("group_id", "user_id"))

wordcount_for_all_users_3d <- full_join(missing, wordcount_for_active_users_3d)

wordcount_for_all_users_3d <- addConditionsCVK2(wordcount_for_all_users_3d)

gini_coeff_3d <- wordcount_for_all_users_3d %>% 
  group_by(group_id) %>% 
  summarize(gini_3d = gini(wordcount_3d)*length(wordcount_3d)/(length(wordcount_3d)-1))

```
### WORDCOUNTS AND GINI AFTER DAY 7
```{r}
# wordcounts after day 7
wordcount_for_active_users_7d <- all_sequences %>% 
  filter(!user_id == "start") %>% 
  filter(period <= 7) %>% 
  group_by(group_id, user_id) %>% 
  summarise(wordcount_7d = sum(wordcount))

# file with all groups and users, set activity_count to 0
add_groups_and_users <- all_groups_and_users %>%
    select(c(group_id, user_id)) %>% 
    mutate(wordcount_7d = 0)

# all inactive users 
missing <- anti_join(add_groups_and_users, wordcount_for_active_users_7d, by = c("group_id", "user_id"))

wordcount_for_all_users_7d <- full_join(missing, wordcount_for_active_users_7d)

wordcount_for_all_users_7d <- addConditionsCVK2(wordcount_for_all_users_7d)

gini_coeff_7d <- wordcount_for_all_users_7d %>% 
  group_by(group_id) %>% 
  summarize(gini_7d = gini(wordcount_7d)*length(wordcount_7d)/(length(wordcount_7d)-1))
```

### WORDCOUNTS AND GINI AFTER DAY 10
```{r}
# wordcounts after day 10
wordcount_for_active_users_10d <- all_sequences %>% 
  filter(!user_id == "start") %>% 
  filter(period <= 10) %>% 
  group_by(group_id, user_id) %>% 
  summarise(wordcount_10d = sum(wordcount))

# file with all groups and users, set activity_count to 0
add_groups_and_users <- all_groups_and_users %>%
    select(c(group_id, user_id)) %>% 
    mutate(wordcount_10d = 0)

# all inactive users 
missing <- anti_join(add_groups_and_users, wordcount_for_active_users_10d, by = c("group_id", "user_id"))

wordcount_for_all_users_10d <- full_join(missing, wordcount_for_active_users_10d)

wordcount_for_all_users_10d <- addConditionsCVK2(wordcount_for_all_users_10d)

gini_coeff_10d <- wordcount_for_all_users_10d %>% 
  group_by(group_id) %>% 
  summarize(gini_10d = gini(wordcount_10d)*length(wordcount_10d)/(length(wordcount_10d)-1))
```

### WORDCOUNTS AND GINI AFTER DAY 12
```{r}
# wordcounts after day 12
wordcount_for_active_users_12d <- all_sequences %>% 
  filter(!user_id == "start") %>% 
  filter(period <= 12) %>% 
  group_by(group_id, user_id) %>% 
  summarise(wordcount_12d = sum(wordcount))

# file with all groups and users, set activity_count to 0
add_groups_and_users <- all_groups_and_users %>%
    select(c(group_id, user_id)) %>% 
    mutate(wordcount_12d = 0)

# all inactive users 
missing <- anti_join(add_groups_and_users, wordcount_for_active_users_12d, by = c("group_id", "user_id"))

wordcount_for_all_users_12d <- full_join(missing, wordcount_for_active_users_12d)

wordcount_for_all_users_12d <- addConditionsCVK2(wordcount_for_all_users_12d)

gini_coeff_12d <- wordcount_for_all_users_12d %>% 
  group_by(group_id) %>% 
  summarize(gini_12d = gini(wordcount_12d)*length(wordcount_12d)/(length(wordcount_12d)-1))
```
### WORDCOUNTS AND GINI AFTER DAY 14
```{r}
# wordcounts after day 14
wordcount_for_active_users_14d <- all_sequences %>% 
  filter(!user_id == "start") %>% 
  filter(period <= 14) %>% 
  group_by(group_id, user_id) %>% 
  summarise(wordcount_14d = sum(wordcount))

# file with all groups and users, set activity_count to 0
add_groups_and_users <- all_groups_and_users %>%
    select(c(group_id, user_id)) %>% 
    mutate(wordcount_14d = 0)

# all inactive users 
missing <- anti_join(add_groups_and_users, wordcount_for_active_users_14d, by = c("group_id", "user_id"))

wordcount_for_all_users_14d <- full_join(missing, wordcount_for_active_users_14d)

wordcount_for_all_users_14d <- addConditionsCVK2(wordcount_for_all_users_14d)

gini_coeff_14d <- wordcount_for_all_users_14d %>% 
  group_by(group_id) %>% 
  summarize(gini_14d = gini(wordcount_14d)*length(wordcount_14d)/(length(wordcount_14d)-1))
```

### GINI INDEX OVER TIME
```{r}
gini_over_time <- merge(gini_coeff_3d, gini_coeff_7d) %>% 
  merge(gini_coeff_10d) %>% 
  merge(gini_coeff_12d) %>% 
  merge(gini_coeff_14d) %>% 
  addConditionsCVK2() %>% 
  addTaskCVK2()
```



