---
title: "CVK 2.0 Task 2"
output: html_notebook
---

```{r}
source("setup.R")
source("util.R")
source("CVK2-util.R")
```

###TODO for new task:
#### read new files
#### adjust condition information
#### adjust start date (task_begin <- as.Date(...))
#### check and remove data (gini, groups, ...) for completely inactive groups (gini = 0)

### READ DATA, GENERATE DATASET
```{r}
### ONCE ###
# complete final models with content for each condition
data_M_H <- fromJSON("/home/doberstein/Dropbox/D/uni/IKARion/CVK 2_0/Task2/Task2_M_H_content.txt")
data_M_H_T <- fromJSON("/home/doberstein/Dropbox/D/uni/IKARion/CVK 2_0/Task2/Task2_M_H_T_content.txt")
data_O_H <- fromJSON("/home/doberstein/Dropbox/D/uni/IKARion/CVK 2_0/Task2/Task2_O_H_content.txt")


### SEQUENCES ###
# unnest sequences from lists to data.frame
sequences_M_H <- data_M_H$group_sequences %>%
  unnest()
sequences_M_H_T <- data_M_H_T$group_sequences %>%
  unnest()
sequences_O_H <- data_O_H$group_sequences %>%
  unnest()

# groups without activities:
# 530 (M_H_T)
# 514 (O_H)


## CLEANING DATASET SINCE THIS TASK WAS LOGGED ON THE THL IKARION SERVER WICH FOR WHATEVER REASON LOGGED SOME ACTIVITIES TWICE ##
## (problem lies with the learning locker which forwards the actions twice)
##  use timestamp / content / both

sequences_M_H <- sequences_M_H %>%
  distinct(content, .keep_all = T)

sequences_M_H_T <- sequences_M_H_T %>%
  distinct(content, .keep_all = T)

sequences_O_H <- sequences_O_H %>%
  distinct(content, .keep_all = T)


# combine all files to a single table
sequences <- bind_rows(list(sequences_M_H, sequences_M_H_T, sequences_O_H)) %>% 
  filter(!content %like% "muss nicht mehr am") %>%         #t2
  filter(!content %like% "das Datum für die Klausur") %>%  #t2
  filter(!content %like% "funktioniert mein Link")         #t2

#write.csv2(sequences, "/home/doberstein/Dropbox/D/uni/IKARion/CVK 2_0/analysis/task2_activities.csv", row.names = F)

### WORK IMBALANCE ###
# extract work imbalances
work_imbalance_M_H <- data_M_H$work_imbalance
work_imbalance_M_H_T <- data_M_H_T$work_imbalance %>% 
  filter(!group_id == 530)
work_imbalance_O_H <- data_O_H$work_imbalance %>% 
  filter(!group_id == 514)



# combine all files to a single table
work_imbalances <- bind_rows(list(work_imbalance_M_H, work_imbalance_M_H_T, work_imbalance_O_H))

# adding condition information #
work_imbalances <- addConditionsCVK2(work_imbalances)

# write.csv2(work_imbalances, "/home/doberstein/Dropbox/D/uni/IKARion/CVK 2_0/analysis/task2_work_imbalances.csv", row.names = F)

### FINAL WIKI weighted wordcounts ###
weighted_wordcount_wiki_M_H <- data_M_H$weighted_wiki_wordcount %>%
  unnest()
weighted_wordcount_wiki_M_H_T <- data_M_H_T$weighted_wiki_wordcount %>%
  unnest()
weighted_wordcount_wiki_O_H <- data_O_H$weighted_wiki_wordcount %>%
  unnest()
# combine all files to a single table
weighted_wiki_wordcounts <- bind_rows(list(weighted_wordcount_wiki_M_H, weighted_wordcount_wiki_M_H_T, weighted_wordcount_wiki_O_H)) %>%
  filter(!group_id %in% c(514, 530)) %>% 
  addConditionsCVK2() 

# write.csv2(weighted_wiki_wordcounts, "/home/doberstein/Dropbox/D/uni/IKARion/CVK 2_0/analysis/task2_weighted_wiki_wordcounts.csv", row.names = F)

### FINAL Forum WORD COUNTS ###
wordcount_share_forum_M_H <- data_M_H$weighted_forum_wordcount %>%
  unnest()
wordcount_share_forum_M_H_T <- data_M_H_T$weighted_forum_wordcount %>%
  unnest()
wordcount_share_forum_O_H <- data_O_H$weighted_forum_wordcount %>%
  unnest()

# combine all files to a single table
forum_shares <- bind_rows(list(wordcount_share_forum_M_H, wordcount_share_forum_M_H_T, wordcount_share_forum_O_H)) %>%
  filter(!group_id %in% c(514, 530)) %>% 
  addConditionsCVK2()

# write.csv2(forum_shares, "/home/doberstein/Dropbox/D/uni/IKARion/CVK 2_0/analysis/task2_forum_shares.csv")

# extract groups and users
users_groups_M_H <- data_M_H$model_metadata$groups %>%
  unnest()
users_groups_M_H_T <- data_M_H_T$model_metadata$groups %>%
  unnest()
users_groups_O_H <- data_O_H$model_metadata$groups %>%
  unnest()

# combine all files to a single table
groups_and_users <- bind_rows(list(users_groups_M_H, users_groups_M_H_T,  users_groups_O_H)) %>%
  subset(select = c("group_id", "name"))
names(groups_and_users)[names(groups_and_users) == 'name'] <- 'user_id'

groups_and_users <- addConditionsCVK2(groups_and_users) %>% 
  filter(!group_id %in% c(514, 530))


# write.csv2(groups_and_users, "/home/doberstein/Dropbox/D/uni/IKARion/CVK 2_0/analysis/task2_groups_and_users.csv")
```

### DATA PREPROCESSING: WIKI WORDCOUNT CALCULATION
```{r}
## ONCE ###
sequences <- sequences %>%
  rowwise() %>%
  mutate(content = gsub("\n", " ", content)) %>%  # delete newlines
  mutate(wordcount = wordcount(content))  # calculate wordcount

### FORUM DATA ###
forum_data <- sequences %>% filter(verb_id == "http://id.tincanapi.com/verb/replied")

### WIKI DATA ###

wiki_data <- sequences %>% filter(verb_id == "http://id.tincanapi.com/verb/updated") %>%
  group_by(group_id) %>%
  arrange(timestamp, .by_group = T) %>%
  mutate(textchange = wordcount - lag(wordcount)) # calculate textchange as difference between current and last revision

# correct value for first revisions (since textchange for first posts are "NA")
firstRevisions <- is.na(wiki_data$textchange)
wiki_data$textchange[firstRevisions] <- wiki_data$wordcount[firstRevisions]

# correct value for revisions that are shorter than the last on (change negative numbers to 0)
negativeWordcounts <- wiki_data$textchange < 0
length(which(negativeWordcounts[negativeWordcounts==TRUE]))
wiki_data$textchange[negativeWordcounts] <- 0

# replace 'wordcount' with 'textchange'
wiki_data <- wiki_data %>%
  subset(select = - wordcount)

names(wiki_data)[names(wiki_data) == 'textchange'] <- 'wordcount'

### Analyze together ###
sequences2 <- bind_rows(list(forum_data, wiki_data)) %>%
  group_by(group_id) %>%
  arrange(timestamp, .by_group = T)

sequences <- sequences2

#write.csv2(sequences2, "/home/doberstein/Dropbox/D/uni/IKARion/CVK 2_0/analysis/task2_activities.csv")

### find largest deletes: wiki post with highest negative wordcount ###
# wiki_data2 <- wiki_data %>%
#   arrange(textchange)
#
# ind <- which(wiki_data2$textchange == -460)
# rows <- lapply(ind, function(wiki_data2) (wiki_data2-5):(wiki_data2+5))
# # With unlist() you get all relevant rows
# d1 <- wiki_data2[unlist(rows),]
```






### ADDING START ELEMENT TO EACH SEQUENCE ###
#############################################

```{r}
all_sequences <- sequences %>% 
  addConditionsCVK2() 

#***
anydate(as.numeric(all_sequences[1,]$timestamp))
#***

task_begin <- as.Date("2019-11-04")

all_sequences <- all_sequences %>% 
  mutate(day = anydate(as.numeric(timestamp))) %>% 
  mutate(period = as.numeric(anydate(as.numeric(timestamp)) - task_begin)+1) %>% 
  mutate(type = ifelse(object_type == "http://id.tincanapi.com/activitytype/forum-topic", "forum", "wiki"))
  

# (real) time in forum: Montag, 26. November 2018, 15:37
# timestamp in activity sequence: 1543243054 = Montag, 26. November 2018, 14:37
# -> timestamp has to be real-time - 3600

# Task 1
# task_start:   1571652000    (21.10.19 10:00 AM UTC) (11:00 Uhr lokal)

# task_end:     1572822300    (03.11.19 23:05 AM UTC) (00:05 Uhr lokal)

# Task 2
# task_start:   1572865200   (04.11.19 11:00 AM UTC) (12:00 Uhr lokal)
# task_end:     1574031900    (17.11.19 23:05 AM UTC) (00:05 Uhr lokal)



# start + end timestamps
task_start <- 1572865200
task_end <- 1574031900

# timestamp for first activity
all_sequences[1,]$timestamp

# timestamp for last activity
all_sequences[nrow(all_sequences),]$timestamp

first_activity <- all_sequences[1,]
col_names <- names(first_activity)

# complete start element for each task
general_start_activity <- data.frame(as.list(c(group_id=1, content="start", object_id="start", object_name="start", object_type="start", timestamp=0, user_id="start", verb_id="start", wordcount=0, condition="test", day="1970-01-01", period=1, type="start", class="start")))
names(general_start_activity) <- col_names

task_start_activity <- data.frame(as.list(c(group_id=1, content="start", object_id="start", object_name="start", object_type="start", timestamp=task_start, user_id="start", verb_id="start", wordcount=0, condition="test", day="2019-11-04", period=1, type="start", class="start")))
names(task_start_activity) <- col_names

all_sequences_with_start <- data.frame()

addStartElement <- function(df) {
  
  #browser()

  first_row <- df[1,]
  sequence <- rbind(first_row, df)

  sequence[1,]$content <- "start"
  sequence[1,]$object_id <- "start"
  sequence[1,]$object_name <- "start"
  sequence[1,]$object_type <- "start"
  sequence[1,]$user_id <- "start"
  sequence[1,]$verb_id <- "start"
  sequence[1,]$wordcount <- 0
  sequence[1,]$condition <- df[1,]$condition
  sequence[1,]$type <- "start"
  sequence[1,]$class <- "start"

  ### ADD TASK INFO ###
  #####################
  
  # task 1:
  if(df[1,]$group_id %in% c(486:505)) {
    sequence[1,]$timestamp <- as.numeric(as.character(task_start_activity$timestamp))
    sequence[1,]$day <- "2019-10-21"
    sequence[1,]$period <- 1
  }
  
  if(df[1,]$group_id %in% c(514:531)) {
    sequence[1,]$timestamp <- as.numeric(as.character(task_start_activity$timestamp))
    sequence[1,]$day <- "2019-11-04"
    sequence[1,]$period <- 1
  }
  
  all_sequences_with_start <<- rbind(all_sequences_with_start, sequence)

}

all_sequences %>%
  group_by(group_id) %>%
  do(addStartElement(.))

#write.csv2(all_sequences_with_start, "/home/doberstein/Dropbox/D/uni/IKARion/CVK 2_0/analysis/t2_activities_with_start.csv", row.names = F)

all_sequences <- read.csv2("/home/doberstein/Dropbox/D/uni/IKARion/CVK 2_0/analysis/t2_activities_with_start.csv", stringsAsFactors = F) %>% addTaskCVK2()
  

typeof(all_sequences[1,]$day)

all_sequences$day <- as.Date(all_sequences$day, format = "%Y-%m-%d")

typeof(all_sequences[1,]$day)

```
### Average wordcount for wiki activities
```{r}
mean(wiki_data$wordcount)
```
### Average wordcount for forum activities
```{r}
mean(forum_data$wordcount)
```
# ACTIVITY COUNT FOR CONDITION
```{r}

cond_activity_count <- all_sequences %>% 
  group_by(group_id) %>% 
  summarise(activity_count = n()) %>% 
  addConditionsCVK2()

cond_activity_count <- cond_activity_count %>% 
  group_by(condition) %>% 
  summarise(average_activity_count = mean(activity_count), sd = sd(activity_count))

cond_activity_count
```

# WORDCOUNT IN FINAL WIKI REVISIONS
```{r}
wiki_wordcount <- wiki_data %>% 
  group_by(group_id) %>% 
  slice(c(n())) %>%
  ungroup() %>% 
  dplyr::rowwise() %>% 
  mutate(wordcount = wordcount(content)) %>% 
  addConditionsCVK2()

# mean(wiki_wordcount$wordcount)
# median(wiki_wordcount$wordcount)
# sd(wiki_wordcount$wordcount)


wordcount_by_condition <- wiki_wordcount %>% 
  group_by(condition) %>% 
  summarise(average_wordcount = mean(wordcount), sd = sd(wordcount), max = max(wordcount), min = min(wordcount))

wordcount_by_condition
```


# GINI INDEX OVER TIME
```{r}
sequences <- all_sequences %>% 
  filter(!type == "start")

# filter sub-sequences to only contain relevant activities (timewise)
seq_day1 <- sequences %>% 
  filter(period <= 1)
seq_day2 <- sequences %>% 
  filter(period <= 2)
seq_day3 <- sequences %>% 
  filter(period <= 3)
seq_day4 <- sequences %>% 
  filter(period <= 4)
seq_day5 <- sequences %>% 
  filter(period <= 5)
seq_day6 <- sequences %>% 
  filter(period <= 6)
seq_day7 <- sequences %>% 
  filter(period <= 7)
seq_day8 <- sequences %>% 
  filter(period <= 8)
seq_day9 <- sequences %>% 
  filter(period <= 9)
seq_day10 <- sequences %>% 
  filter(period <= 10)
seq_day11 <- sequences %>% 
  filter(period <= 11)
seq_day12 <- sequences %>% 
  filter(period <= 12)
seq_day13 <- sequences %>% 
  filter(period <= 13)
seq_day14 <- sequences %>% 
  filter(period <= 14)


wordcounts_day1 <- calculateWordcount(seq_day1) %>% 
  addConditionsCVK2()
wordcounts_day2 <- calculateWordcount(seq_day2)%>% 
  addConditionsCVK2()
wordcounts_day3 <- calculateWordcount(seq_day3)%>% 
  addConditionsCVK2()
wordcounts_day4 <- calculateWordcount(seq_day4)%>% 
  addConditionsCVK2()
wordcounts_day5 <- calculateWordcount(seq_day5)%>% 
  addConditionsCVK2()
wordcounts_day6 <- calculateWordcount(seq_day6)%>% 
  addConditionsCVK2()
wordcounts_day7 <- calculateWordcount(seq_day7)%>% 
  addConditionsCVK2()
wordcounts_day8 <- calculateWordcount(seq_day8)%>% 
  addConditionsCVK2()
wordcounts_day9 <- calculateWordcount(seq_day9)%>% 
  addConditionsCVK2()
wordcounts_day10 <- calculateWordcount(seq_day10)%>% 
  addConditionsCVK2()
wordcounts_day11 <- calculateWordcount(seq_day11)%>% 
  addConditionsCVK2()
wordcounts_day12 <- calculateWordcount(seq_day12)%>% 
  addConditionsCVK2()
wordcounts_day13 <- calculateWordcount(seq_day13)%>% 
  addConditionsCVK2()
wordcounts_day14 <- calculateWordcount(seq_day14)%>% 
  addConditionsCVK2()

# add inactive users with wordcount = 0
# get groups and users
groups_and_users <- read.csv2("/home/doberstein/Dropbox/D/uni/IKARion/CVK 2_0/analysis/task2_groups_and_users.csv", stringsAsFactors = F) %>% 
  subset(select = -X) %>%
  mutate(wordcount = 0)

# add user that unenrolled from course: xznJc2qD3s60qjB6Mazeng==
# users appears in work_balance, wiki and forum wordcount + sequence but not in group in metadata
#groups_and_users[nrow(groups_and_users) + 1,] = list(165, "xznJc2qD3s60qjB6Mazeng==", "M", 0)

missing_day1 <- anti_join(groups_and_users, wordcounts_day1, by = c("group_id", "user_id", "condition"))
missing_day2 <- anti_join(groups_and_users, wordcounts_day2, by = c("group_id", "user_id", "condition"))
missing_day3 <- anti_join(groups_and_users, wordcounts_day3, by = c("group_id", "user_id", "condition"))
missing_day4 <- anti_join(groups_and_users, wordcounts_day4, by = c("group_id", "user_id", "condition"))
missing_day5 <- anti_join(groups_and_users, wordcounts_day5, by = c("group_id", "user_id", "condition"))
missing_day6 <- anti_join(groups_and_users, wordcounts_day6, by = c("group_id", "user_id", "condition"))
missing_day7 <- anti_join(groups_and_users, wordcounts_day7, by = c("group_id", "user_id", "condition"))
missing_day8 <- anti_join(groups_and_users, wordcounts_day8, by = c("group_id", "user_id", "condition"))
missing_day9 <- anti_join(groups_and_users, wordcounts_day9, by = c("group_id", "user_id", "condition"))
missing_day10 <- anti_join(groups_and_users, wordcounts_day10, by = c("group_id", "user_id", "condition"))
missing_day11 <- anti_join(groups_and_users, wordcounts_day11, by = c("group_id", "user_id", "condition"))
missing_day12 <- anti_join(groups_and_users, wordcounts_day12, by = c("group_id", "user_id", "condition"))
missing_day13 <- anti_join(groups_and_users, wordcounts_day13, by = c("group_id", "user_id", "condition"))
missing_day14 <- anti_join(groups_and_users, wordcounts_day14, by = c("group_id", "user_id", "condition"))

all_wordcounts_day1 <- full_join(missing_day1, wordcounts_day1, by = c("group_id", "user_id", "condition", "wordcount"))
all_wordcounts_day2 <- full_join(missing_day2, wordcounts_day2, by = c("group_id", "user_id", "condition", "wordcount"))
all_wordcounts_day3 <- full_join(missing_day3, wordcounts_day3, by = c("group_id", "user_id", "condition", "wordcount"))
all_wordcounts_day4 <- full_join(missing_day4, wordcounts_day4, by = c("group_id", "user_id", "condition", "wordcount"))
all_wordcounts_day5 <- full_join(missing_day5, wordcounts_day5, by = c("group_id", "user_id", "condition", "wordcount"))
all_wordcounts_day6 <- full_join(missing_day6, wordcounts_day6, by = c("group_id", "user_id", "condition", "wordcount"))
all_wordcounts_day7 <- full_join(missing_day7, wordcounts_day7, by = c("group_id", "user_id", "condition", "wordcount"))
all_wordcounts_day8 <- full_join(missing_day8, wordcounts_day8, by = c("group_id", "user_id", "condition", "wordcount"))
all_wordcounts_day9 <- full_join(missing_day9, wordcounts_day9, by = c("group_id", "user_id", "condition", "wordcount"))
all_wordcounts_day10 <- full_join(missing_day10, wordcounts_day10, by = c("group_id", "user_id", "condition", "wordcount"))
all_wordcounts_day11 <- full_join(missing_day11, wordcounts_day11, by = c("group_id", "user_id", "condition", "wordcount"))
all_wordcounts_day12 <- full_join(missing_day12, wordcounts_day12, by = c("group_id", "user_id", "condition", "wordcount"))
all_wordcounts_day13 <- full_join(missing_day13, wordcounts_day13, by = c("group_id", "user_id", "condition", "wordcount"))
all_wordcounts_day14 <- full_join(missing_day14, wordcounts_day14, by = c("group_id", "user_id", "condition", "wordcount"))

# calculate gini_coefficients for each day
gini_day1 <- all_wordcounts_day1 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))
gini_day2 <- all_wordcounts_day2 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))
gini_day3 <- all_wordcounts_day3 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))
gini_day4 <- all_wordcounts_day4 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))
gini_day5 <- all_wordcounts_day5 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))
gini_day6 <- all_wordcounts_day6 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))
gini_day7 <- all_wordcounts_day7 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))
gini_day8 <- all_wordcounts_day8 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))
gini_day9 <- all_wordcounts_day9 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))
gini_day10 <- all_wordcounts_day10 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))
gini_day11 <- all_wordcounts_day11 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))
gini_day12 <- all_wordcounts_day12 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))
gini_day13 <- all_wordcounts_day13 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))
gini_day14 <- all_wordcounts_day14 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))


# changing_gini <- gini_day1
# changing_gini$day2 <- gini_day2$gini_index
# changing_gini$day3 <- gini_day3$gini_index
# changing_gini$day4 <- gini_day4$gini_index
# changing_gini$day5 <- gini_day5$gini_index
# changing_gini$day6 <- gini_day6$gini_index
# changing_gini$day7 <- gini_day7$gini_index
# changing_gini$day8 <- gini_day8$gini_index
# changing_gini$day9 <- gini_day9$gini_index
# changing_gini$day10 <- gini_day10$gini_index
# changing_gini$day11 <- gini_day11$gini_index
# changing_gini$day12 <- gini_day12$gini_index
# changing_gini$day13 <- gini_day13$gini_index
# changing_gini$day14 <- gini_day14$gini_index
# 
# names(changing_gini)[names(changing_gini) == 'gini_index'] <- 'day1'

changing_gini <- gini_day1
changing_gini$period = 1

changing_gini <- addValues(changing_gini, gini_day2, 2)
changing_gini <- addValues(changing_gini, gini_day3, 3)
changing_gini <- addValues(changing_gini, gini_day4, 4)
changing_gini <- addValues(changing_gini, gini_day5, 5)
changing_gini <- addValues(changing_gini, gini_day6, 6)
changing_gini <- addValues(changing_gini, gini_day7, 7)
changing_gini <- addValues(changing_gini, gini_day8, 8)
changing_gini <- addValues(changing_gini, gini_day9, 9)
changing_gini <- addValues(changing_gini, gini_day10, 10)
changing_gini <- addValues(changing_gini, gini_day11, 11)
changing_gini <- addValues(changing_gini, gini_day12, 12)
changing_gini <- addValues(changing_gini, gini_day13, 13)
changing_gini <- addValues(changing_gini, gini_day14, 14)

changing_gini <- addConditionsCVK2(changing_gini)

#write.csv2(changing_gini, "/home/doberstein/Dropbox/D/uni/IKARion/CVK 2_0/analysis/task2_changing_gini.csv", row.names = F)

```

### ACTIVITY COUNT OVER TIME
```{r}

activity_counts_day1 <- calculateActivityCount(seq_day1) %>% 
  addConditionsCVK2()
activity_counts_day2 <- calculateActivityCount(seq_day2) %>% 
  addConditionsCVK2()
activity_counts_day3 <- calculateActivityCount(seq_day3) %>% 
  addConditionsCVK2()
activity_counts_day4 <- calculateActivityCount(seq_day4) %>% 
  addConditionsCVK2()
activity_counts_day5 <- calculateActivityCount(seq_day5) %>% 
  addConditionsCVK2()
activity_counts_day6 <- calculateActivityCount(seq_day6) %>% 
  addConditionsCVK2()
activity_counts_day7 <- calculateActivityCount(seq_day7) %>% 
  addConditionsCVK2()
activity_counts_day8 <- calculateActivityCount(seq_day8) %>% 
  addConditionsCVK2()
activity_counts_day9 <- calculateActivityCount(seq_day9) %>% 
  addConditionsCVK2()
activity_counts_day10 <- calculateActivityCount(seq_day10) %>% 
  addConditionsCVK2()
activity_counts_day11 <- calculateActivityCount(seq_day11) %>% 
  addConditionsCVK2()
activity_counts_day12 <- calculateActivityCount(seq_day12) %>% 
  addConditionsCVK2()
activity_counts_day13 <- calculateActivityCount(seq_day13) %>% 
  addConditionsCVK2()
activity_counts_day14 <- calculateActivityCount(seq_day14) %>% 
  addConditionsCVK2()

changing_activity_count <- activity_counts_day1
changing_activity_count$period = 1

changing_activity_count <- addValues(changing_activity_count, activity_counts_day2, 2)
changing_activity_count <- addValues(changing_activity_count, activity_counts_day3, 3)
changing_activity_count <- addValues(changing_activity_count, activity_counts_day4, 4)
changing_activity_count <- addValues(changing_activity_count, activity_counts_day5, 5)
changing_activity_count <- addValues(changing_activity_count, activity_counts_day6, 6)
changing_activity_count <- addValues(changing_activity_count, activity_counts_day7, 7)
changing_activity_count <- addValues(changing_activity_count, activity_counts_day8, 8)
changing_activity_count <- addValues(changing_activity_count, activity_counts_day9, 9)
changing_activity_count <- addValues(changing_activity_count, activity_counts_day10, 10)
changing_activity_count <- addValues(changing_activity_count, activity_counts_day11, 11)
changing_activity_count <- addValues(changing_activity_count, activity_counts_day12, 12)
changing_activity_count <- addValues(changing_activity_count, activity_counts_day13, 13)
changing_activity_count <- addValues(changing_activity_count, activity_counts_day14, 14)

#write.csv2(changing_activity_count, "/home/doberstein/Dropbox/D/uni/IKARion/CVK 2_0/analysis/task2_changing_activity_count.csv", row.names = F)
```

### WORD COUNT OVER TIME
```{r}

word_counts_day1 <- calculateWordCount(seq_day1) %>% 
  addConditionsCVK2()
word_counts_day2 <- calculateWordCount(seq_day2) %>% 
  addConditionsCVK2()
word_counts_day3 <- calculateWordCount(seq_day3) %>% 
  addConditionsCVK2()
word_counts_day4 <- calculateWordCount(seq_day4) %>% 
  addConditionsCVK2()
word_counts_day5 <- calculateWordCount(seq_day5) %>% 
  addConditionsCVK2()
word_counts_day6 <- calculateWordCount(seq_day6) %>% 
  addConditionsCVK2()
word_counts_day7 <- calculateWordCount(seq_day7) %>% 
  addConditionsCVK2()
word_counts_day8 <- calculateWordCount(seq_day8) %>% 
  addConditionsCVK2()
word_counts_day9 <- calculateWordCount(seq_day9) %>% 
  addConditionsCVK2()
word_counts_day10 <- calculateWordCount(seq_day10) %>% 
  addConditionsCVK2()
word_counts_day11 <- calculateWordCount(seq_day11) %>% 
  addConditionsCVK2()
word_counts_day12 <- calculateWordCount(seq_day12) %>% 
  addConditionsCVK2()
word_counts_day13 <- calculateWordCount(seq_day13) %>% 
  addConditionsCVK2()
word_counts_day14 <- calculateWordCount(seq_day14) %>% 
  addConditionsCVK2()

changing_word_count <- word_counts_day1
changing_word_count$period = 1

changing_word_count <- addValues(changing_word_count, word_counts_day2, 2)
changing_word_count <- addValues(changing_word_count, word_counts_day3, 3)
changing_word_count <- addValues(changing_word_count, word_counts_day4, 4)
changing_word_count <- addValues(changing_word_count, word_counts_day5, 5)
changing_word_count <- addValues(changing_word_count, word_counts_day6, 6)
changing_word_count <- addValues(changing_word_count, word_counts_day7, 7)
changing_word_count <- addValues(changing_word_count, word_counts_day8, 8)
changing_word_count <- addValues(changing_word_count, word_counts_day9, 9)
changing_word_count <- addValues(changing_word_count, word_counts_day10, 10)
changing_word_count <- addValues(changing_word_count, word_counts_day11, 11)
changing_word_count <- addValues(changing_word_count, word_counts_day12, 12)
changing_word_count <- addValues(changing_word_count, word_counts_day13, 13)
changing_word_count <- addValues(changing_word_count, word_counts_day14, 14)

# write.csv2(changing_word_count, "/home/doberstein/Dropbox/D/uni/IKARion/CVK 2_0/analysis/task2_changing_word_count.csv", row.names = F)
```

#wordcounts for each group after x days
```{r}
# # for each group
# group_word_counts_day1 <- wordcounts_day1%>% 
#   group_by(group_id) %>% 
#   summarise(group_wordcount = sum(wordcount))
# 
# group_word_counts_day2 <- wordcounts_day2%>% 
#   group_by(group_id) %>% 
#   summarise(group_wordcount = sum(wordcount))

# average overall
overall_average_wordcount_day1 <- all_wordcounts_day1 %>% 
  group_by(group_id) %>% 
  summarise(group_wordcount_day1 = sum(wordcount))

overall_average_wordcount_day2 <- all_wordcounts_day2 %>% 
  group_by(group_id) %>% 
  summarise(group_wordcount_day2 = sum(wordcount))

overall_average_wordcount_day3 <- all_wordcounts_day3 %>% 
  group_by(group_id) %>% 
  summarise(group_wordcount_day3 = sum(wordcount))

overall_average_wordcount_day4 <- all_wordcounts_day4 %>% 
  group_by(group_id) %>% 
  summarise(group_wordcount_day4 = sum(wordcount))

overall_average_wordcount_day5 <- all_wordcounts_day5 %>% 
  group_by(group_id) %>% 
  summarise(group_wordcount_day5 = sum(wordcount))

overall_average_wordcount_day6 <- all_wordcounts_day6 %>% 
  group_by(group_id) %>% 
  summarise(group_wordcount_day6 = sum(wordcount))

overall_average_wordcount_day7 <- all_wordcounts_day7 %>% 
  group_by(group_id) %>% 
  summarise(group_wordcount_day7 = sum(wordcount))

overall_average_wordcount_day8 <- all_wordcounts_day8 %>% 
  group_by(group_id) %>% 
  summarise(group_wordcount_day8 = sum(wordcount))

overall_average_wordcount_day9 <- all_wordcounts_day9 %>% 
  group_by(group_id) %>% 
  summarise(group_wordcount_day9 = sum(wordcount))

overall_average_wordcount_day10 <- all_wordcounts_day10 %>% 
  group_by(group_id) %>% 
  summarise(group_wordcount_day10 = sum(wordcount))

overall_average_wordcount_day11 <- all_wordcounts_day11 %>% 
  group_by(group_id) %>% 
  summarise(group_wordcount_day11 = sum(wordcount))

overall_average_wordcount_day12 <- all_wordcounts_day12 %>% 
  group_by(group_id) %>% 
  summarise(group_wordcount_day12 = sum(wordcount))

overall_average_wordcount_day13 <- all_wordcounts_day13 %>% 
  group_by(group_id) %>% 
  summarise(group_wordcount_day13 = sum(wordcount))

overall_average_wordcount_day14 <- all_wordcounts_day14 %>% 
  group_by(group_id) %>% 
  summarise(group_wordcount_day14 = sum(wordcount))


overall_wordcounts <- full_join(overall_average_wordcount_day1, overall_average_wordcount_day2) %>% 
  full_join(overall_average_wordcount_day3) %>% 
  full_join(overall_average_wordcount_day4) %>%
  full_join(overall_average_wordcount_day5) %>%
  full_join(overall_average_wordcount_day6) %>%
  full_join(overall_average_wordcount_day7) %>%
  full_join(overall_average_wordcount_day8) %>%
  full_join(overall_average_wordcount_day9) %>%
  full_join(overall_average_wordcount_day10) %>%
  full_join(overall_average_wordcount_day11) %>%
  full_join(overall_average_wordcount_day12) %>%
  full_join(overall_average_wordcount_day13) %>%
  full_join(overall_average_wordcount_day14)

#write.csv2(overall_wordcounts, "/home/doberstein/Dropbox/D/uni/IKARion/CVK 2_0/analysis/task2_group_wordcounts.csv", row.names = F)
```
## ACTIVITY DISTRIBUTION OVER DAYS BY CONDITION
```{r}
activity_distribution_for_condition <- changing_activity_count %>% 
  group_by(period) %>% 
  group_by(condition, add = T) %>% 
  summarise(accum_activity_count = sum(activity_count))
```

```{r}
ggplot(activity_distribution_for_condition, aes(x=period, y=accum_activity_count, group=condition)) +
  geom_line(aes(color=condition))+
  geom_point(aes(color=condition))+
  #scale_x_continuous(labels = days, breaks = c(1:14))
  scale_x_continuous(breaks = c(1:14))
```


## WORKDISTRIBUTION OVER DAYS BY CONDITION
```{r}
work_distribution_for_condition <- changing_gini %>% 
  filter(!is.na(gini_index)) %>% 
  group_by(period) %>% 
  group_by(condition, add = T) %>% 
  summarise(average_gini = mean(gini_index), sd = sd(gini_index))
```

```{r}
ggplot(work_distribution_for_condition, aes(x=period, y=average_gini, group=condition))+
  geom_line(aes(color=condition))+
  geom_point(aes(color=condition))+
  scale_x_continuous(breaks = c(1:14))

```

## WORD COUNTS OVER DAYS BY CONDITION
```{r}
word_counts_for_condition <- changing_word_count %>% 
  group_by(period) %>% 
  group_by(condition, add = T) %>% 
  summarise(accum_word_count = sum(word_count))
```

```{r}
ggplot(word_counts_for_condition, aes(x=period, y=accum_word_count, group=condition)) +
  geom_line(aes(color=condition))+
  geom_point(aes(color=condition))+
  #scale_x_continuous(labels = days, breaks = c(1:14))
  scale_x_continuous(breaks = c(1:14))
```

