---
title: "R Notebook"
output: html_notebook
---

**Read the data**

```{r}
require(dplyr)
require(magrittr)
require(DT)
require(tidyr)
#library(psych)

data <- read.csv2("/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/CKV analysis - sequence - survey/decision_tree_table.csv", stringsAsFactors = F) 


#%>% rename(cos_sim_rank=rank, cos_sim_norm_rank=norm.rank)
names(data)
```

**Dependent varialbes: wordcount, zufried09, zufried10, gini**

*1. ANOVA: Assuming homogeneous variances*

Note: The variance homogenity precondition is not met since cluster 2 has a much higher variance in concept coverate than the other two.

```{r}
aov(wordcount ~ membership_manual, data=data) %>% summary
```


```{r}
aov(Zufried_09 ~ membership_manual, data=data) %>% summary
```
```{r}
aov(Zufried_10 ~ membership_manual, data=data) %>% summary
```

```{r}
aov(gini_index ~ membership_manual, data=data) %>% summary
```

t-test
```{r}
#pairwise.t.test(data$, data$clustering_pam3_manual, p.adjust.method = "none")
t.test(wordcount ~ membership_manual, data = data)
```

```{r}
kruskal.test(wordcount ~ membership_manual, data = data)
```

```{r}
data %>% group_by(membership_manual) %>% 
  summarise(var_wordcount = sd(wordcount))

data %>% 
  filter(membership_manual == 1) %>% 
  hist(.$wordcount)

data1 <- data %>% 
  filter(membership_manual == 1)

hist(data1$wordcount,breaks = 20)

data2 <- data %>% 
  filter(membership_manual == 2)

hist(data2$wordcount, breaks = 10)
# hist(data$wordcount %>% filter(membership_manual  1))
# 
# class(data$membership_manual)
```

```{r}
t.test(Zufried_09 ~ membership_manual, data = data)
```
```{r}
t.test(Zufried_10 ~ membership_manual, data = data)
```
```{r}
t.test(gini_index ~ membership_manual, data = data)
```
```{r}
names(data)
```

### ICWL 2019 paper data for correlation here ###
#################################################

```{r}
    
data %>% subset(select = c(wordcount, Zufried_09, Zufried_10, gini_index, coordination_count_fh, coordination_count, gap_count, gap_count_fh)) %>%
  as.matrix() %>%
  cor()

cor.test(data$Zufried_09, data$gini_index, method = "spearman", exact = F)
#cor.test(data$Zufried_09, data$gini_index, method = "pearson")
#cor.test(data$Zufried_09, data$gini_index)

cor.test(data$Zufried_10, data$gini_index, method = "spearman")

cor.test(data$Zufried_09, data$wordcount, method = "spearman")
cor.test(data$Zufried_10, data$wordcount, method = "spearman")
cor.test(data$Zufried_10, data$gini_index, method = "spearman")
=cor.test(data$Zufried_10, data$coordination_count, method = "spearman")

cor.test(data$wordcount, data$gini_index, method = "spearman")


cor.test(data$coordination_count_fh, data$wordcount, method = "spearman")
    
```

```{r}
lm(Zufried_09 ~ gini_index + coordination_count_fh, data = data) %>% summary

lm(gini_index ~ coordination_count_fh, data = data) %>% summary
```
```{r}
table(data$membership_manual, data$condition) %>% chisq.test()


chisq.test()
```

### ICWL 2019 significance tests here ###
#########################################

man whitney test since witha small sample size (29 groups) a normality of the distributions inside the clusters can not be guaranteed
-> man whitney test works on ranks, which is less problematic for such a smaple size and distribution 

### Mann-Whitney Test ###
#########################
```{r}
#wilcox.test(mpg ~ am, data=mtcars) 
#t.test(wordcount ~ membership_manual, data = data)

#wilcox.test(wordcount ~ membership_manual, data = data)
#wilcox.test(gini_index ~ membership_manual, data = data)
#wilcox.test(Zufried_10 ~ membership_manual, data = data)
wilcox.test(Zufried_09 ~ membership_manual, data = data)

```

*** signif. tests ***
data:  wordcount by membership_manual
W = 26, p-value = 0.0009205
data:  Zufried_09 by membership_manual
W = 34.5, p-value = 0.005729
data:  Zufried_10 by membership_manual
W = 39, p-value = 0.01065
data:  gini_index by membership_manual
W = 147, p-value = 0.01617
*** ***


