---
title: "CVK Kurs - SozPsy Analyse"
output: html_notebook
---

## INSTALL LIBRARIES (ONCE)
```{r}
# install.packages("dplyr")
# install.packages("reldist")
```



## LOAD NECESSARY LIBRARYS
```{r}
library(reldist)
library(dplyr)
```

## SOME USEFUL FUNCTIONS
```{r}
# writing data frame to csv file
# write.csv2(<data table name>, "<path/filename.csv>")
# write.csv2(all_sequences, "/home/doberstein/Desktop/all_sequences.csv", row.names = F)

# reading data from csv file into R data frame
# <data frame name> <- read.csv2("<path/filename.csv", stringsAsFactors = F)
# all_groups_and_users <- read.csv2("/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/t4_t5_t6_activities_with_start.csv", stringsAsFactors = F)

```

##UTIL
```{r}
# add conditions based on group IDs
addConditions <- function(df) {
  if (nrow(df) > 0) {
    df$condition <- NA
    
    # Task1
    df$condition[df$group_id %in% c(154:159)] <- "Ko"
    df$condition[df$group_id %in% c(160:165)] <- "M"
    df$condition[df$group_id %in% c(166:171)] <- "MG"
    df$condition[df$group_id %in% c(172:174)] <- "KR"
    
    # Task2
    df$condition[df$group_id %in% c(187:192)] <- "Ko"
    df$condition[df$group_id %in% c(193:197)] <- "M"
    df$condition[df$group_id %in% c(198:202)] <- "MG"
    
    # Task3
    df$condition[df$group_id %in% c(211:215)] <- "Ko"
    df$condition[df$group_id %in% c(216:219)] <- "M"
    df$condition[df$group_id %in% c(221:224)] <- "MG"
    
    # Task4
    df$condition[df$group_id %in% c(230:235)] <- "N_A"
    df$condition[df$group_id %in% c(237:242)] <- "W_A"
    
    # Task5
    df$condition[df$group_id %in% c(247:252)] <- "N_A"
    df$condition[df$group_id %in% c(254:259)] <- "W_A"
    
    # Task6
    df$condition[df$group_id %in% c(265:270)] <- "N_A"
    df$condition[df$group_id %in% c(272:277)] <- "W_A"
  }
  
  df
}

# add tasks based on group IDs
addTask <- function(df) {
  if (nrow(df) > 0) {
    df$task <- NA
    
    # Task1
    df$task[df$group_id %in% c(154:174)] <- "task1"
    
    # Task2
    df$task[df$group_id %in% c(187:202)] <- "task2"
    
    # Task3
    df$task[df$group_id %in% c(211:224)] <- "task3"
    
    # Task4
    df$task[df$group_id %in% c(230:242)] <- "task4"
    
    # Task5
    df$task[df$group_id %in% c(247:259)] <- "task5"
    
    # Task6
    df$task[df$group_id %in% c(265:277)] <- "task6"
  }
  
  df
}
```


## LOAD DATASET
### Dataset contains all relevant activities (forum posts / wiki updates) for grouptasks 4,5,6 for the conditions:
### N_A: No Agent
### W_A: With Agent 

### Task4: Common_Ground
### GruppenIDs: 230 - 242

### Task5: Informationsaustausch
### GruppenIDs: 247 - 259

### Task6: Soziale Interdependenz
### GruppenIDs: 265 - 277

### For each group a "start" activity has been added to the "activity sequence" so that the startpoint for the task is apparent (e.g. to find initial inactivity)
```{r}

### NOTE ###
# replace path to file (e.g. "/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/t4_t5_t6_activities_with_start.csv") with path to local file 
# example local path: "C:/Users/Filipa/Dokumente/IKARion/CVK MOOC/data"
# example for data read:
  # all_sequences <- read.csv2("C:/Users/Filipa/Dokumente/IKARion/CVK MOOC/data", stringsAsFactors = F) %>% subset(select=-c(X, class))


all_sequences <- read.csv2("/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/t4_t5_t6_activities_with_start.csv", stringsAsFactors = F) %>% 
  subset(select=-c(X, class)) %>% 
  addTask()

# columns: 
# names(all_sequences)

# "group_id"    : group id (int)
# "content"     : text content of the activity. complete message for forum activities, complete wiki revision for wiki activities
# "object_id"   :
# "object_name" :
# "object_type" :
# "timestamp"   : unix timestamp stating the time that the activity occured
# "user_id"     : user id (anonymized)
# "verb_id"     :
# "wordcount"   : number of words for forum activities, difference between number of words in current and last revision for wiki articles
# "condition"   : N_A: "No Agent""; W_A "With Agent""
# "day"         : day that the activity occured
# "period"      : relative day that the activity occured counted from the task beginning (1-14 for all tasks)
# "type"        : wiki / forum
# "task"        : Gruppenaufgabe



# read data containing all users with groups and condition (Groups for "Keine R체ckmeldung" are omitted)
all_groups_and_users <- read.csv2("/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/all_groups_and_users_task4_6.csv", stringsAsFactors = F) %>% 
  addTask()
```

### GET ACTIVITY DATA FOR ONE GROUP
```{r}
group_230 <- all_sequences %>% 
  filter(group_id == 230)

group_230

# write as csv
#write.csv2(group_230, "/home/doberstein/Desktop/group_230.csv", row.names = F)
```

### FILTER OUT START ACTIVITY
```{r}
one_group <- all_sequences %>% 
  filter(group_id == 230) %>% 
  filter(!user_id == "start") 
```

### ACTIVITY COUNT PER USER PER GROUP
```{r}
activity_count_for_active_users <- all_sequences %>% 
  filter(!user_id == "start") %>% 
  group_by(group_id, user_id) %>% 
  summarise(activity_count = n())

activity_count_for_active_users
```
### ADDING INACTIVE USERS
```{r}
# file with all groups and users, set activity_count to 0
add_groups_and_users <- all_groups_and_users %>%
  dplyr::select(c(group_id, user_id)) %>% 
    mutate(activity_count = 0)

# all inactive users 
missing <- anti_join(add_groups_and_users, activity_count_for_active_users, by = c("group_id", "user_id"))

activity_count_for_all_users <- full_join(missing, activity_count_for_active_users)

activity_count_for_all_users
```

# IKARion Logfiles zu Wordcount in Forum und Wiki

### WORDCOUNT FOR EACH USER
```{r}
wordcount_for_active_users <- all_sequences %>% 
  filter(!user_id == "start") %>% 
  # filter(period <= 3) %>%  filter out activities after day 3
  # filter(period <= 7) %>%  filter out activities after day 3
  # filter(period <= 10) %>%  filter out activities after day 3
  # filter(period <= 12) %>%  filter out activities after day 3
  # filter(period <= 14) %>%  filter out activities after day 3
  group_by(group_id, user_id) %>% 
  summarise(overall_wordcount = sum(wordcount))

# file with all groups and users, set activity_count to 0
add_groups_and_users <- all_groups_and_users %>%
    dplyr::select(c(group_id, user_id)) %>% 
    mutate(overall_wordcount = 0)

# all inactive users 
missing <- anti_join(add_groups_and_users, wordcount_for_active_users, by = c("group_id", "user_id"))

wordcount_for_all_users <- full_join(missing, wordcount_for_active_users)

wordcount_for_all_users <- addConditions(wordcount_for_all_users)
```

## FORUM WORDCOUNT FOR EACH USER
```{r}
forum_wordcount_for_active_users <- all_sequences %>% 
  filter(!user_id == "start") %>% 
  filter(type == "forum") %>% 
  group_by(group_id, user_id) %>% 
  summarise(forum_wordcount = sum(wordcount))

# file with all groups and users, set activity_count to 0
add_groups_and_users <- all_groups_and_users %>%
    dplyr::select(c(group_id, user_id)) %>% 
    mutate(forum_wordcount = 0)

# all inactive users 
missing <- anti_join(add_groups_and_users, forum_wordcount_for_active_users, by = c("group_id", "user_id"))

forum_wordcount_for_all_users <- full_join(missing, forum_wordcount_for_active_users) %>% 
  addConditions()

```

## WIKI WORDCOUNT FOR EACH USER
```{r}
wiki_wordcount_for_active_users <- all_sequences %>% 
  filter(!user_id == "start") %>% 
  filter(type == "wiki") %>% 
  group_by(group_id, user_id) %>% 
  summarise(wiki_wordcount = sum(wordcount))

# file with all groups and users, set activity_count to 0
add_groups_and_users <- all_groups_and_users %>%
    dplyr::select(c(group_id, user_id)) %>% 
    mutate(wiki_wordcount = 0)

# all inactive users 
missing <- anti_join(add_groups_and_users, wiki_wordcount_for_active_users, by = c("group_id", "user_id"))

wiki_wordcount_for_all_users <- full_join(missing, wiki_wordcount_for_active_users) %>% 
  addConditions()
```

## WORDCOUNT FOR EACH USER AFTER 7 DAYS
```{r}
wordcount_for_active_users_7d <- all_sequences %>% 
  filter(!user_id == "start") %>% 
  filter(period <= 7) %>% # filter out activities that occured after day 7
  group_by(group_id, user_id) %>% 
  summarise(overall_wordcount_7d = sum(wordcount))

# file with all groups and users, set activity_count to 0
add_groups_and_users <- all_groups_and_users %>%
    dplyr::select(c(group_id, user_id)) %>% 
    mutate(overall_wordcount_7d = 0)

# all inactive users 
missing <- anti_join(add_groups_and_users, wordcount_for_active_users_7d, by = c("group_id", "user_id"))

wordcount_for_all_users_7d <- full_join(missing, wordcount_for_active_users_7d) %>% 
  addConditions()

wordcount_for_all_users_7d
```

## MERGING DATAFRAMES
```{r}
wordcount_for_all_users
forum_wordcount_for_all_users
wiki_wordcount_for_all_users
wordcount_for_all_users_7d

complete_wordcount_data <- merge(wordcount_for_all_users, forum_wordcount_for_all_users) %>% 
  merge(wiki_wordcount_for_all_users) %>% 
  merge(wordcount_for_all_users_7d)
  


```

#IKARion Zeitabstand zwischen Forenbeitr채gen

## TIME BETWEEN FORUM POSTS
```{r}
forum_latency <- all_sequences %>% 
  filter(type == "forum" | type == "start") %>% 
  group_by(group_id) %>% 
  mutate(forum_latency_sec = timestamp - lag(timestamp)) %>% 
  addConditions()
```

## AVERAGE TIME BETWEEN FORUM POSTS BY GROUP
```{r}
forum_latency_by_group <- forum_latency %>% 
  filter(!user_id == "start") %>% 
  group_by(group_id) %>% 
  summarise(average_latency = mean(forum_latency_sec))

forum_activity_count_by_group <- forum_latency %>% 
  filter(!user_id == "start") %>% 
  group_by(group_id) %>% 
  summarise(forum_activity_count = n())

forum_data <- merge(forum_latency_by_group, forum_activity_count_by_group) %>% 
  addConditions()

```


## TIME BETWEEN WIKI UPDATES
```{r}
wiki_latency <- all_sequences %>% 
  filter(type == "wiki" | type == "start") %>% 
  group_by(group_id) %>% 
  mutate(wiki_latency_sec = timestamp - lag(timestamp))
```

## TIME BETWEEN ANY KIND OF ACTIVITY
```{r}
activity_latency <- all_sequences %>% 
  group_by(group_id) %>% 
  mutate(activity_latency_sec = timestamp - lag(timestamp))

## maximal period of inactivity over all groups (in days)
max(activity_latency$activity_latency_sec, na.rm = T) / 60 / 60 / 24

```

## Aktivit채ten f체r Themenblock 4
### Task4: Common Ground 
### GruppenIDs: 154 - 174
```{r}
# all task 4 activities
task4_activities <- all_sequences %>% 
  filter(group_id %in% c(230:242)) %>% 
  filter(!user_id == "start")

# all task 4 forum activities
task4_forum_activities <- task4_activities %>% 
  filter(type == "forum")

# all task 4 wiki activities
task4_wiki_activities <- task4_activities %>% 
  filter(type == "wiki")

# all task 4 activities for condition "No Agent" ("N_A")
task4_activities_N_A <- task4_activities %>% 
  filter(condition == "N_A")

# all task 4 activities for one group (154)
task4_activities_230 <- task4_activities %>% 
  filter(group_id == 230)
```


# IKARion Logfiles zu Gini-Koeffizient in Forum und Wiki
```{r}
# gini calculation for all activities (forum + wiki combined) for complete task (14 days)

# (already done above, see calculation for variable: "wordcount_for_all_users")
gini_coeff_overall <- wordcount_for_all_users %>% 
  group_by(group_id) %>% 
  summarize(gini_overall = gini(overall_wordcount)*length(overall_wordcount)/(length(overall_wordcount)-1))

gini_coeff_overall_active_users <- wordcount_for_all_users %>% 
  filter(overall_wordcount > 0) %>% 
  group_by(group_id) %>% 
  summarize(gini_overall = gini(overall_wordcount)*length(overall_wordcount)/(length(overall_wordcount)-1))

```

### WORDCOUNTS AND GINI AFTER DAY 3
```{r}
# wordcounts after day 3
wordcount_for_active_users_3d <- all_sequences %>% 
  filter(!user_id == "start") %>% 
  filter(period <= 3) %>% 
  group_by(group_id, user_id) %>% 
  summarise(wordcount_3d = sum(wordcount))

# file with all groups and users, set activity_count to 0
add_groups_and_users <- all_groups_and_users %>%
    dplyr::select(c(group_id, user_id)) %>% 
    mutate(wordcount_3d = 0)

# all inactive users 
missing <- anti_join(add_groups_and_users, wordcount_for_active_users_3d, by = c("group_id", "user_id"))

wordcount_for_all_users_3d <- full_join(missing, wordcount_for_active_users_3d)

wordcount_for_all_users_3d <- addConditions(wordcount_for_all_users_3d)

gini_coeff_3d <- wordcount_for_all_users_3d %>% 
  group_by(group_id) %>% 
  summarize(gini_3d = gini(wordcount_3d)*length(wordcount_3d)/(length(wordcount_3d)-1))

```
### WORDCOUNTS AND GINI AFTER DAY 7
```{r}
# wordcounts after day 7
wordcount_for_active_users_7d <- all_sequences %>% 
  filter(!user_id == "start") %>% 
  filter(period <= 7) %>% 
  group_by(group_id, user_id) %>% 
  summarise(wordcount_7d = sum(wordcount))

# file with all groups and users, set activity_count to 0
add_groups_and_users <- all_groups_and_users %>%
    dplyr::select(c(group_id, user_id)) %>% 
    mutate(wordcount_7d = 0)

# all inactive users 
missing <- anti_join(add_groups_and_users, wordcount_for_active_users_7d, by = c("group_id", "user_id"))

wordcount_for_all_users_7d <- full_join(missing, wordcount_for_active_users_7d)

wordcount_for_all_users_7d <- addConditions(wordcount_for_all_users_7d)

gini_coeff_7d <- wordcount_for_all_users_7d %>% 
  group_by(group_id) %>% 
  summarize(gini_7d = gini(wordcount_7d)*length(wordcount_7d)/(length(wordcount_7d)-1))
```

### WORDCOUNTS AND GINI AFTER DAY 10
```{r}
# wordcounts after day 10
wordcount_for_active_users_10d <- all_sequences %>% 
  filter(!user_id == "start") %>% 
  filter(period <= 10) %>% 
  group_by(group_id, user_id) %>% 
  summarise(wordcount_10d = sum(wordcount))

# file with all groups and users, set activity_count to 0
add_groups_and_users <- all_groups_and_users %>%
    dplyr::select(c(group_id, user_id)) %>% 
    mutate(wordcount_10d = 0)

# all inactive users 
missing <- anti_join(add_groups_and_users, wordcount_for_active_users_10d, by = c("group_id", "user_id"))

wordcount_for_all_users_10d <- full_join(missing, wordcount_for_active_users_10d)

wordcount_for_all_users_10d <- addConditions(wordcount_for_all_users_10d)

gini_coeff_10d <- wordcount_for_all_users_10d %>% 
  group_by(group_id) %>% 
  summarize(gini_10d = gini(wordcount_10d)*length(wordcount_10d)/(length(wordcount_10d)-1))
```

### WORDCOUNTS AND GINI AFTER DAY 12
```{r}
# wordcounts after day 12
wordcount_for_active_users_12d <- all_sequences %>% 
  filter(!user_id == "start") %>% 
  filter(period <= 12) %>% 
  group_by(group_id, user_id) %>% 
  summarise(wordcount_12d = sum(wordcount))

# file with all groups and users, set activity_count to 0
add_groups_and_users <- all_groups_and_users %>%
    dplyr::select(c(group_id, user_id)) %>% 
    mutate(wordcount_12d = 0)

# all inactive users 
missing <- anti_join(add_groups_and_users, wordcount_for_active_users_12d, by = c("group_id", "user_id"))

wordcount_for_all_users_12d <- full_join(missing, wordcount_for_active_users_12d)

wordcount_for_all_users_12d <- addConditions(wordcount_for_all_users_12d)

gini_coeff_12d <- wordcount_for_all_users_12d %>% 
  group_by(group_id) %>% 
  summarize(gini_12d = gini(wordcount_12d)*length(wordcount_12d)/(length(wordcount_12d)-1))
```
### WORDCOUNTS AND GINI AFTER DAY 14
```{r}
# wordcounts after day 14
wordcount_for_active_users_14d <- all_sequences %>% 
  filter(!user_id == "start") %>% 
  filter(period <= 14) %>% 
  group_by(group_id, user_id) %>% 
  summarise(wordcount_14d = sum(wordcount))

# file with all groups and users, set activity_count to 0
add_groups_and_users <- all_groups_and_users %>%
    dplyr::select(c(group_id, user_id)) %>% 
    mutate(wordcount_14d = 0)

# all inactive users 
missing <- anti_join(add_groups_and_users, wordcount_for_active_users_14d, by = c("group_id", "user_id"))

wordcount_for_all_users_14d <- full_join(missing, wordcount_for_active_users_14d)

wordcount_for_all_users_14d <- addConditions(wordcount_for_all_users_14d)

gini_coeff_14d <- wordcount_for_all_users_14d %>% 
  group_by(group_id) %>% 
  summarize(gini_14d = gini(wordcount_14d)*length(wordcount_14d)/(length(wordcount_14d)-1))
```

### GINI INDEX OVER TIME
```{r}
gini_over_time <- merge(gini_coeff_3d, gini_coeff_7d) %>% 
  merge(gini_coeff_10d) %>% 
  merge(gini_coeff_12d) %>% 
  merge(gini_coeff_14d) %>% 
  addConditions()
```


```{r}
# View(gini_over_time)
```




