---
title: "CVK MOOC Analysis Task1"
output: html_notebook
---

```{r}
source("setup.R")
source("util.R")
```

###TODO for new task:
####read new files
####adjust condition information
####adjust start date (task_begin <- as.Date(...))


### READ DATA, GENERATE DATASET
```{r}
### ONCE ###
# complete final models with content for each condition
data_Ko <- fromJSON("/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/Task1/Task1_IntModelle_Ko_content_updated.txt")
data_M <- fromJSON("/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/Task1/Task1_IntModelle_M_content_updated.txt")
data_MG <- fromJSON("/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/Task1/Task1_IntModelle_MG_content_updated.txt")
data_KR <- fromJSON("/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/Task1/Task1_IntModelle_K_R_content_updated.txt")


### SEQUENCES ###
# unnest sequences from lists to data.frame
sequences_Ko <- data_Ko$group_sequences %>%
  unnest()
sequences_M <- data_M$group_sequences %>%
  unnest()
sequences_MG <- data_MG$group_sequences %>%
  unnest()
sequences_KR <- data_KR$group_sequences %>%
  unnest()

# combine all files to a single table
sequences <- bind_rows(list(sequences_Ko, sequences_M, sequences_MG, sequences_KR))

write.csv2(sequences, "/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/task1_activities.csv")

### WORK IMBALANCE ###
# extract work imbalances
work_imbalance_Ko <- data_Ko$work_imbalance
work_imbalance_M <- data_M$work_imbalance
work_imbalance_MG <- data_MG$work_imbalance
work_imbalance_KR <- data_KR$work_imbalance

# combine all files to a single table
work_imbalances <- bind_rows(list(work_imbalance_Ko, work_imbalance_M, work_imbalance_MG, work_imbalance_KR))

# adding condition information #
work_imbalances <- addConditions(work_imbalances)

write.csv2(work_imbalances, "/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/task1_work_imbalances.csv")

### FINAL WIKI WORD COUNTS ###
wordcount_wiki_Ko <- data_Ko$text_contributions_wiki %>%
  unnest()
wordcount_wiki_M <- data_M$text_contributions_wiki %>%
  unnest()
wordcount_wiki_MG <- data_MG$text_contributions_wiki %>%
  unnest()
wordcount_wiki_KR <- data_KR$text_contributions_wiki %>%
  unnest()

# combine all files to a single table
wiki_wordcounts <- bind_rows(list(wordcount_wiki_Ko, wordcount_wiki_M, wordcount_wiki_MG, wordcount_wiki_KR)) %>%
  addConditions()

write.csv2(wiki_wordcounts, "/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/task1_wiki_wordcounts.csv")

### FINAL Forum WORD COUNTS ###
wordcount_forum_Ko <- data_Ko$text_contributions_forum %>%
  unnest()
wordcount_forum_M <- data_M$text_contributions_forum %>%
  unnest()
wordcount_forum_MG <- data_MG$text_contributions_forum %>%
  unnest()
wordcount_forum_KR <- data_KR$text_contributions_forum %>%
  unnest()

# combine all files to a single table
forum_wordcounts <- bind_rows(list(wordcount_forum_Ko, wordcount_forum_M, wordcount_forum_MG, wordcount_forum_KR)) %>%
  addConditions()

write.csv2(forum_wordcounts, "/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/task1_forum_wordcounts.csv")

# extract groups and users
users_groups_Ko <- data_Ko$model_metadata$groups %>%
  unnest()
users_groups_M <- data_M$model_metadata$groups %>%
  unnest()
users_groups_MG <- data_MG$model_metadata$groups %>%
  unnest()
users_groups_KR <- data_KR$model_metadata$groups %>%
  unnest()

# combine all files to a single table
groups_and_users <- bind_rows(list(users_groups_Ko, users_groups_M, users_groups_MG, users_groups_KR)) %>%
  subset(select = c("group_id", "name"))
names(groups_and_users)[names(groups_and_users) == 'name'] <- 'user_id'

groups_and_users <- addConditions(groups_and_users)


write.csv2(groups_and_users, "/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/task1_groups_and_users.csv")

```

### DATA PREPROCESSING: WIKI WORDCOUNT CALCULATION
```{r}
## ONCE ###
sequences <- read.csv2("/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/task1_activities.csv", stringsAsFactors = F) %>%
  subset(select=-X) %>%
  rowwise() %>%
  mutate(content = gsub("\n", " ", content)) %>%  # delete newlines
  mutate(wordcount = wordcount(content))  # calculate wordcount

### FORUM DATA ###
forum_data <- sequences %>% filter(verb_id == "http://id.tincanapi.com/verb/replied")

### WIKI DATA ###

wiki_data <- sequences %>% filter(verb_id == "http://id.tincanapi.com/verb/updated") %>%
  group_by(group_id) %>%
  arrange(timestamp, .by_group = T) %>%
  mutate(textchange = wordcount - lag(wordcount)) # calculate textchange as difference between current and last revision

# correct value for first revisions (since textchange for first posts are "NA")
firstRevisions <- is.na(wiki_data$textchange)
wiki_data$textchange[firstRevisions] <- wiki_data$wordcount[firstRevisions]

# correct value for revisions that are shorter than the last on (change negative numbers to 0)
negativeWordcounts <- wiki_data$textchange < 0
length(which(negativeWordcounts[negativeWordcounts==TRUE]))
wiki_data$textchange[negativeWordcounts] <- 0

# replace 'wordcount' with 'textchange'
wiki_data <- wiki_data %>%
  subset(select = - wordcount)

names(wiki_data)[names(wiki_data) == 'textchange'] <- 'wordcount'

### Analyze together ###
sequences2 <- bind_rows(list(forum_data, wiki_data)) %>%
  group_by(group_id) %>%
  arrange(timestamp, .by_group = T)

write.csv2(sequences2, "/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/task1_activities.csv")

### find largest deletes: wiki post with highest negative wordcount ###
# wiki_data2 <- wiki_data2 %>%
#   arrange(textchange)
#
# ind <- which(wiki_data2$textchange == -460)
# rows <- lapply(ind, function(wiki_data2) (wiki_data2-5):(wiki_data2+5))
# # With unlist() you get all relevant rows
# d1 <- wiki_data2[unlist(rows),]
```

### READ PREPROCESSED DATASET; ADD EXPERIMANTAL CONDITIONS TO GROUPS; ADD DATE TO ACTIVITIES

```{r}
### READ DATA ###
sequences <- read.csv2("/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/task1_activities.csv", stringsAsFactors = F) %>% 
  subset(select=-X) %>% 
  addConditions()



### adding dates as days
### adding period (first day = 1; last day = 14)
### adding type (forum, wiki)

task_begin <- as.Date("2018-10-15")

sequences <- sequences %>% 
  mutate(day = anydate(timestamp)) %>% 
  mutate(period = as.numeric(anydate(timestamp) - task_begin)+1) %>% 
  mutate(type = ifelse(object_type == "http://id.tincanapi.com/activitytype/forum-topic", "forum", "wiki"))
  

write.csv2(sequences, "/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/task1_activities_2.csv")

### FORUM DATA ###
forum_data <- sequences %>% filter(verb_id == "http://id.tincanapi.com/verb/replied")

### WIKI DATA ###

wiki_data <- sequences %>% filter(verb_id == "http://id.tincanapi.com/verb/updated")
```



# BASIC STATS 
```{r}
### (MEAN, SD, ...)
```

<span style="color:blue">IKARion MOOC 2:1; MERCUR MOOC 3:1</span>

### Average wordcount for wiki activities
```{r}
mean(wiki_data$wordcount)
median(wiki_data$wordcount)
```

### Average wordcount for forum activities
```{r}
mean(forum_data$wordcount)
```

```{r}
# # stats for wiki data
# median(wiki_data$wordcount)
# sd(wiki_data$wordcount)
# 
# # stats for forum data
# median(forum_data$wordcount)
# sd(forum_data$wordcount)
# 
# # number of activities per group
# activity_count <- sequences %>%
#   group_by(group_id) %>%
#   summarise(activity_count = n())

```

# ACTIVITY COUNT FOR CONDITION
##<span style="color:red">Ko = Kontrollgruppe</span>

##<span style="color:red">KR = Keine Rückmeldung</span>

##<span style="color:red">M = Mirroring</span>

##<span style="color:red">MG = Mirroring&Guiding</span>

<span style="color:blue">M, M&G more active than Ko, high sd</span>
```{r}
cond_activity_count <- sequences %>% 
  group_by(group_id) %>% 
  summarise(activity_count = n()) %>% 
  addConditions()

cond_activity_count <- cond_activity_count %>% 
  group_by(condition) %>% 
  summarise(average_activity_count = mean(activity_count), sd = sd(activity_count))

cond_activity_count
```

```{r}
ggplot(data=cond_activity_count, aes(x=condition, y=average_activity_count)) +
  geom_bar(stat="identity", ,fill="steelblue") + 
  geom_errorbar(aes(ymin=average_activity_count-sd, ymax=average_activity_count+sd), width=.2,
                 position=position_dodge(.9))
```

# WORDCOUNT IN FINAL WIKI REVISIONS
<span style="color:blue">Ko highest wordcount, all groups (but one) above minimum</span>
```{r}
wiki_wordcount <- wiki_data %>% 
  group_by(group_id) %>% 
  slice(c(n())) %>%
  ungroup() %>% 
  dplyr::rowwise() %>% 
  mutate(wordcount = wordcount(content))

# mean(wiki_wordcount$wordcount)
# median(wiki_wordcount$wordcount)
# sd(wiki_wordcount$wordcount)


wordcount_by_condition <- wiki_wordcount %>% 
  group_by(condition) %>% 
  summarise(average_wordcount = mean(wordcount), sd = sd(wordcount), max = max(wordcount), min = min(wordcount))

wordcount_by_condition
```
```{r}
ggplot(data=wordcount_by_condition, aes(x=condition, y=average_wordcount)) +
  geom_bar(stat="identity",fill="steelblue") + 
  geom_errorbar(aes(ymin=average_wordcount-sd, ymax=average_wordcount+sd), width=.2,
                 position=position_dodge(.9))
```


```{r}
## ACTIVITY DISTRIBUTION OVER DAYS
activity_distribution <- sequences %>% 
  group_by(period) %>% 
  summarise(activities_per_day = n())
```



```{r}
days <- c("Mo", "Di","Mi","Do","Fr","Sa","So","Mo","Di","Mi","Do","Fr","Sa","So")

p <- ggplot(data=activity_distribution, aes(x=period, y=activities_per_day)) +
  geom_bar(stat="identity",fill="steelblue")+
  #geom_text(aes(label=activities_per_day), vjust=1.6, color="white", size=3.5)+ # inside bars
  geom_text(aes(label=activities_per_day), vjust=-0.3, size=3.5)+
  scale_x_continuous(labels = days, breaks = c(1:14))+
  theme_minimal()

#p

#ggsave("activity_distribution.png")

```

# ACTIVITY DISTRIBUTION OVER DAYS BY TYPE
<span style="color:blue">beginning week 2: spike in forum activity</span>
<span style="color:blue">towards the deadline: spike in wiki activity</span>
```{r}
activity_distribution_for_type <- sequences %>% 
  group_by(period) %>% 
  group_by(type, add = T) %>% 
  summarise(activities_per_day = n())
```

```{r}
ggplot(data=activity_distribution_for_type, aes(x=period, y=activities_per_day, fill = type)) +
  geom_bar(stat="identity")+
  #geom_text(aes(label=activities_per_day), vjust=1.6, color="white", size=3.5)+ # inside bars
  #geom_text(aes(label=activities_per_day), vjust=-0.3, size=3.5)+
  #geom_text(aes(y=label_ypos, label=activities_per_day), vjust=1.6, color="white", size=3.5)+
  scale_fill_brewer(palette="Set1")+
  scale_x_continuous(labels = days, breaks = c(1:14))+
  theme_minimal()

#ggsave("activity_distribution_for_type.png")
```

# ACTIVITY DISTRIBUTION OVER DAYS BY CONDITION
<span style="color:blue">spike in MG on the last day</span>
<span style="color:blue"></span>
```{r}
activity_distribution_for_condition <- sequences %>% 
  group_by(period) %>% 
  group_by(condition, add = T) %>% 
  summarise(activities_per_day = n())
```

```{r}
ggplot(data=activity_distribution_for_condition, aes(x=period, y=activities_per_day, fill = condition)) +
  geom_bar(stat="identity")+
  #geom_text(aes(label=activities_per_day), vjust=1.6, color="white", size=3.5)+ # inside bars
  #geom_text(aes(label=activities_per_day), vjust=-0.3, size=3.5)+
  #geom_text(aes(y=label_ypos, label=activities_per_day), vjust=1.6, color="white", size=3.5)+
  scale_fill_brewer(palette="Set1")+
  scale_x_continuous(labels = days, breaks = c(1:14))+
  theme_minimal()

#ggsave("activity_distribution_for_type.png")
```

```{r}
p <- ggplot(data=activity_distribution_for_condition, aes(x=period, y=activities_per_day, fill = condition)) +
  geom_bar(stat="identity",position=position_dodge() )+
  #geom_text(aes(label=activities_per_day), vjust=1.6, color="white", size=3.5)+ # inside bars
  #geom_text(aes(label=activities_per_day), vjust=-0.3, size=3.5)+
  #geom_text(aes(y=label_ypos, label=activities_per_day), vjust=1.6, color="white", size=3.5)+
  scale_fill_brewer(palette="Set1")+
  scale_x_continuous(labels = days, breaks = c(1:14))+
  theme_minimal()

#p
```


```{r}
# ggplot(data=activity_distribution_for_type, aes(x=period, y=activities_per_day, fill = type)) +
#   geom_bar(stat="identity")+
#   #geom_text(aes(label=activities_per_day), vjust=1.6, color="white", size=3.5)+ # inside bars
#   #geom_text(aes(label=activities_per_day), vjust=-0.3, size=3.5)+
#   #geom_text(aes(y=label_ypos, label=activities_per_day), vjust=1.6, color="white", size=3.5)+
#   scale_fill_brewer(palette="Set1")+
#   scale_x_continuous(labels = days, breaks = c(1:14))+
#   theme_minimal() + 
#   coord_polar()
```

```{r}
### READ DATA ###
task1_work_imbalance <- read.csv2("/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/task1_work_imbalances.csv", stringsAsFactors = F) %>% 
  subset(select=-X)
task1_wiki_wordcounts <- read.csv2("/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/task1_wiki_wordcounts.csv", stringsAsFactors = F) %>% 
  subset(select=-X)
task1_forum_wordcounts <- read.csv2("/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/task1_forum_wordcounts.csv", stringsAsFactors = F) %>% 
  subset(select=-X)
```

```{r}
wiki_wordcounts <- task1_wiki_wordcounts
names(wiki_wordcounts)[names(wiki_wordcounts) == 'user_wordcount'] <- 'wiki_wordcount'

forum_wordcounts <- task1_forum_wordcounts
names(forum_wordcounts)[names(forum_wordcounts) == 'user_wordcount'] <- 'forum_wordcount'

task1_wordcounts <- merge(wiki_wordcounts, forum_wordcounts, by = c("user_id", "group_id", "condition")) %>% 
  rowwise() %>% 
  mutate(overall_wordcount = sum(wiki_wordcount, forum_wordcount))

```

```{r}
### GINI INDEX OVER TIME

# filter sub-sequences to only contain relevant activities (timewise)
seq_day1 <- sequences %>% 
  filter(period <= 1)
seq_day2 <- sequences %>% 
  filter(period <= 2)
seq_day3 <- sequences %>% 
  filter(period <= 3)
seq_day4 <- sequences %>% 
  filter(period <= 4)
seq_day5 <- sequences %>% 
  filter(period <= 5)
seq_day6 <- sequences %>% 
  filter(period <= 6)
seq_day7 <- sequences %>% 
  filter(period <= 7)
seq_day8 <- sequences %>% 
  filter(period <= 8)
seq_day9 <- sequences %>% 
  filter(period <= 9)
seq_day10 <- sequences %>% 
  filter(period <= 10)
seq_day11 <- sequences %>% 
  filter(period <= 11)
seq_day12 <- sequences %>% 
  filter(period <= 12)
seq_day13 <- sequences %>% 
  filter(period <= 13)
seq_day14 <- sequences %>% 
  filter(period <= 14)


wordcounts_day1 <- calculateWordcount(seq_day1) %>% 
  addConditions()
wordcounts_day2 <- calculateWordcount(seq_day2)%>% 
  addConditions()
wordcounts_day3 <- calculateWordcount(seq_day3)%>% 
  addConditions()
wordcounts_day4 <- calculateWordcount(seq_day4)%>% 
  addConditions()
wordcounts_day5 <- calculateWordcount(seq_day5)%>% 
  addConditions()
wordcounts_day6 <- calculateWordcount(seq_day6)%>% 
  addConditions()
wordcounts_day7 <- calculateWordcount(seq_day7)%>% 
  addConditions()
wordcounts_day8 <- calculateWordcount(seq_day8)%>% 
  addConditions()
wordcounts_day9 <- calculateWordcount(seq_day9)%>% 
  addConditions()
wordcounts_day10 <- calculateWordcount(seq_day10)%>% 
  addConditions()
wordcounts_day11 <- calculateWordcount(seq_day11)%>% 
  addConditions()
wordcounts_day12 <- calculateWordcount(seq_day12)%>% 
  addConditions()
wordcounts_day13 <- calculateWordcount(seq_day13)%>% 
  addConditions()
wordcounts_day14 <- calculateWordcount(seq_day14)%>% 
  addConditions()

# add inactive users with wordcount = 0
# get groups and users
groups_and_users <- read.csv2("/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/task1_groups_and_users.csv", stringsAsFactors = F) %>% 
  subset(select = -X) %>%
  mutate(wordcount = 0)

# add user that unenrolled from course: xznJc2qD3s60qjB6Mazeng==
# users appears in work_balance, wiki and forum wordcount + sequence but not in group in metadata
# USER WAS ADDED MANUALLY TO "Task1_IntModelle_M_content_updated.txt"
# groups_and_users[nrow(groups_and_users) + 1,] = list(165, "xznJc2qD3s60qjB6Mazeng==", "M", 0)

missing_day1 <- anti_join(groups_and_users, wordcounts_day1, by = c("group_id", "user_id", "condition"))
missing_day2 <- anti_join(groups_and_users, wordcounts_day2, by = c("group_id", "user_id", "condition"))
missing_day3 <- anti_join(groups_and_users, wordcounts_day3, by = c("group_id", "user_id", "condition"))
missing_day4 <- anti_join(groups_and_users, wordcounts_day4, by = c("group_id", "user_id", "condition"))
missing_day5 <- anti_join(groups_and_users, wordcounts_day5, by = c("group_id", "user_id", "condition"))
missing_day6 <- anti_join(groups_and_users, wordcounts_day6, by = c("group_id", "user_id", "condition"))
missing_day7 <- anti_join(groups_and_users, wordcounts_day7, by = c("group_id", "user_id", "condition"))
missing_day8 <- anti_join(groups_and_users, wordcounts_day8, by = c("group_id", "user_id", "condition"))
missing_day9 <- anti_join(groups_and_users, wordcounts_day9, by = c("group_id", "user_id", "condition"))
missing_day10 <- anti_join(groups_and_users, wordcounts_day10, by = c("group_id", "user_id", "condition"))
missing_day11 <- anti_join(groups_and_users, wordcounts_day11, by = c("group_id", "user_id", "condition"))
missing_day12 <- anti_join(groups_and_users, wordcounts_day12, by = c("group_id", "user_id", "condition"))
missing_day13 <- anti_join(groups_and_users, wordcounts_day13, by = c("group_id", "user_id", "condition"))
missing_day14 <- anti_join(groups_and_users, wordcounts_day14, by = c("group_id", "user_id", "condition"))

all_wordcounts_day1 <- full_join(missing_day1, wordcounts_day1, by = c("group_id", "user_id", "condition", "wordcount"))
all_wordcounts_day2 <- full_join(missing_day2, wordcounts_day2, by = c("group_id", "user_id", "condition", "wordcount"))
all_wordcounts_day3 <- full_join(missing_day3, wordcounts_day3, by = c("group_id", "user_id", "condition", "wordcount"))
all_wordcounts_day4 <- full_join(missing_day4, wordcounts_day4, by = c("group_id", "user_id", "condition", "wordcount"))
all_wordcounts_day5 <- full_join(missing_day5, wordcounts_day5, by = c("group_id", "user_id", "condition", "wordcount"))
all_wordcounts_day6 <- full_join(missing_day6, wordcounts_day6, by = c("group_id", "user_id", "condition", "wordcount"))
all_wordcounts_day7 <- full_join(missing_day7, wordcounts_day7, by = c("group_id", "user_id", "condition", "wordcount"))
all_wordcounts_day8 <- full_join(missing_day8, wordcounts_day8, by = c("group_id", "user_id", "condition", "wordcount"))
all_wordcounts_day9 <- full_join(missing_day9, wordcounts_day9, by = c("group_id", "user_id", "condition", "wordcount"))
all_wordcounts_day10 <- full_join(missing_day10, wordcounts_day10, by = c("group_id", "user_id", "condition", "wordcount"))
all_wordcounts_day11 <- full_join(missing_day11, wordcounts_day11, by = c("group_id", "user_id", "condition", "wordcount"))
all_wordcounts_day12 <- full_join(missing_day12, wordcounts_day12, by = c("group_id", "user_id", "condition", "wordcount"))
all_wordcounts_day13 <- full_join(missing_day13, wordcounts_day13, by = c("group_id", "user_id", "condition", "wordcount"))
all_wordcounts_day14 <- full_join(missing_day14, wordcounts_day14, by = c("group_id", "user_id", "condition", "wordcount"))

# calculate gini_coefficients for each day
gini_day1 <- all_wordcounts_day1 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))
gini_day2 <- all_wordcounts_day2 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))
gini_day3 <- all_wordcounts_day3 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))
gini_day4 <- all_wordcounts_day4 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))
gini_day5 <- all_wordcounts_day5 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))
gini_day6 <- all_wordcounts_day6 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))
gini_day7 <- all_wordcounts_day7 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))
gini_day8 <- all_wordcounts_day8 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))
gini_day9 <- all_wordcounts_day9 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))
gini_day10 <- all_wordcounts_day10 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))
gini_day11 <- all_wordcounts_day11 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))
gini_day12 <- all_wordcounts_day12 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))
gini_day13 <- all_wordcounts_day13 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))
gini_day14 <- all_wordcounts_day14 %>% 
  group_by(group_id) %>% 
  summarise(gini_index = gini(wordcount)*length(wordcount)/(length(wordcount)-1))

changing_gini <- gini_day1
changing_gini$period = 1

changing_gini <- addValues(changing_gini, gini_day2, 2)
changing_gini <- addValues(changing_gini, gini_day3, 3)
changing_gini <- addValues(changing_gini, gini_day4, 4)
changing_gini <- addValues(changing_gini, gini_day5, 5)
changing_gini <- addValues(changing_gini, gini_day6, 6)
changing_gini <- addValues(changing_gini, gini_day7, 7)
changing_gini <- addValues(changing_gini, gini_day8, 8)
changing_gini <- addValues(changing_gini, gini_day9, 9)
changing_gini <- addValues(changing_gini, gini_day10, 10)
changing_gini <- addValues(changing_gini, gini_day11, 11)
changing_gini <- addValues(changing_gini, gini_day12, 12)
changing_gini <- addValues(changing_gini, gini_day13, 13)
changing_gini <- addValues(changing_gini, gini_day14, 14)

changing_gini <- addConditions(changing_gini)

write.csv2(changing_gini, "/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/task1_changing_gini.csv")


```

```{r}

activity_counts_day1 <- calculateActivityCount(seq_day1) %>% 
  addConditions()
activity_counts_day2 <- calculateActivityCount(seq_day2) %>% 
  addConditions()
activity_counts_day3 <- calculateActivityCount(seq_day3) %>% 
  addConditions()
activity_counts_day4 <- calculateActivityCount(seq_day4) %>% 
  addConditions()
activity_counts_day5 <- calculateActivityCount(seq_day5) %>% 
  addConditions()
activity_counts_day6 <- calculateActivityCount(seq_day6) %>% 
  addConditions()
activity_counts_day7 <- calculateActivityCount(seq_day7) %>% 
  addConditions()
activity_counts_day8 <- calculateActivityCount(seq_day8) %>% 
  addConditions()
activity_counts_day9 <- calculateActivityCount(seq_day9) %>% 
  addConditions()
activity_counts_day10 <- calculateActivityCount(seq_day10) %>% 
  addConditions()
activity_counts_day11 <- calculateActivityCount(seq_day11) %>% 
  addConditions()
activity_counts_day12 <- calculateActivityCount(seq_day12) %>% 
  addConditions()
activity_counts_day13 <- calculateActivityCount(seq_day13) %>% 
  addConditions()
activity_counts_day14 <- calculateActivityCount(seq_day14) %>% 
  addConditions()

changing_activity_count <- activity_counts_day1
changing_activity_count$period = 1

changing_activity_count <- addValues(changing_activity_count, activity_counts_day2, 2)
changing_activity_count <- addValues(changing_activity_count, activity_counts_day3, 3)
changing_activity_count <- addValues(changing_activity_count, activity_counts_day4, 4)
changing_activity_count <- addValues(changing_activity_count, activity_counts_day5, 5)
changing_activity_count <- addValues(changing_activity_count, activity_counts_day6, 6)
changing_activity_count <- addValues(changing_activity_count, activity_counts_day7, 7)
changing_activity_count <- addValues(changing_activity_count, activity_counts_day8, 8)
changing_activity_count <- addValues(changing_activity_count, activity_counts_day9, 9)
changing_activity_count <- addValues(changing_activity_count, activity_counts_day10, 10)
changing_activity_count <- addValues(changing_activity_count, activity_counts_day11, 11)
changing_activity_count <- addValues(changing_activity_count, activity_counts_day12, 12)
changing_activity_count <- addValues(changing_activity_count, activity_counts_day13, 13)
changing_activity_count <- addValues(changing_activity_count, activity_counts_day14, 14)

write.csv2(changing_activity_count, "/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/task1_changing_activity_count.csv")


```

## ACTIVITY DISTRIBUTION OVER DAYS BY CONDITION
<span style="color:blue">little activity in week one</span>
<span style="color:blue">more activities in groups with condition in the end</span>
```{r}
activity_distribution_for_condition <- changing_activity_count %>% 
  group_by(period) %>% 
  group_by(condition, add = T) %>% 
  summarise(accum_activity_count = sum(activity_count))
```

```{r}
ggplot(activity_distribution_for_condition, aes(x=period, y=accum_activity_count, group=condition)) +
  geom_line(aes(color=condition))+
  geom_point(aes(color=condition))+
  scale_x_continuous(labels = days, breaks = c(1:14))

```

# WORKDISTRIBUTION FOR FINAL RESULTS

## WORK IMBALANCE BY CONDITION
<span style="color:blue">similar in all groups, condition M has fairest work distribution</span>
```{r}

work_imbalance_for_condition <- task1_work_imbalance %>%
  group_by(condition) %>% 
  summarise(average_gini_index = mean(gini_index), sd = sd(gini_index))

work_imbalance_for_condition
```
```{r}
ggplot(data=work_imbalance_for_condition, aes(x=condition, y=average_gini_index)) +
  geom_bar(stat="identity",fill="steelblue") + 
  geom_errorbar(aes(ymin=average_gini_index-sd, ymax=average_gini_index+sd), width=.2,
                 position=position_dodge(.9))
```


```{r}
# ## FORUM WORDCOUNTS BY CONDITION
# 
# forum_wordcount_by_condition <- forum_wordcounts %>%
#   group_by(condition) %>% 
#   summarise(average_forum_wordcount = mean(forum_wordcount), sd = sd(forum_wordcount))
# 
# ggplot(data=forum_wordcount_by_condition, aes(x=condition, y=average_forum_wordcount)) +
#   geom_bar(stat="identity",fill="steelblue") + 
#   geom_errorbar(aes(ymin=average_forum_wordcount-sd, ymax=average_forum_wordcount+sd), width=.2,
#                  position=position_dodge(.9))
  
```

```{r}
# ## WIKI WORDCOUNTS BY CONDITION
# 
# wiki_wordcount_by_condition <- wiki_wordcounts %>%
#   group_by(condition) %>% 
#   summarise(average_wiki_wordcount = mean(wiki_wordcount), sd = sd(wiki_wordcount))
# 
# ggplot(data=wiki_wordcount_by_condition, aes(x=condition, y=average_wiki_wordcount)) +
#   geom_bar(stat="identity",fill="steelblue") + 
#   geom_errorbar(aes(ymin=average_wiki_wordcount-sd, ymax=average_wiki_wordcount+sd), width=.2,
#                  position=position_dodge(.9))
  
```


```{r}
# ## OVERALL WORDCOUNTS BY CONDITION
# wordcount_by_condition <- task1_wordcounts %>%
#   group_by(condition) %>% 
#   summarise(average_wordcount = mean(overall_wordcount), sd = sd(overall_wordcount))
# 
# ggplot(data=wordcount_by_condition, aes(x=condition, y=average_wordcount)) +
#   geom_bar(stat="identity",fill="steelblue") + 
#   geom_errorbar(aes(ymin=average_wordcount-sd, ymax=average_wordcount+sd), width=.2,
#                  position=position_dodge(.9))
  
```


## WORKDISTRIBUTION OVER DAYS BY CONDITION
<span style="color:blue">Ko: in the beginning of week 2: distribution is getting more unfair</span>
<span style="color:blue">similar in condition MG</span>
<span style="color:blue">condtition M relatively stable</span>
```{r}
work_distribution_for_condition <- changing_gini %>% 
  filter(!is.na(gini_index)) %>% 
  group_by(period) %>% 
  group_by(condition, add = T) %>% 
  summarise(average_gini = mean(gini_index), sd = sd(gini_index))
```

```{r}
ggplot(work_distribution_for_condition, aes(x=period, y=average_gini, group=condition)) +
  geom_line(aes(color=condition))+
  geom_point(aes(color=condition))+
  scale_x_continuous(labels = days, breaks = c(1:14))

```

```{r}
# 1) accum activity count only for wiki activities
# 2) closer look at wiki activities in the last 3-4 days

# 1) wiki activities
```

```{r}
# filter sub-sequences to only contain relevant activities (timewise) in wiki

wiki_seq_day1 <- sequences %>% 
  filter(type == "wiki") %>% 
  filter(period <= 1) 
wiki_seq_day2 <- sequences %>% 
  filter(type == "wiki") %>% 
  filter(period <= 2)
wiki_seq_day3 <- sequences %>% 
  filter(type == "wiki") %>%
  filter(period <= 3)
wiki_seq_day4 <- sequences %>% 
  filter(type == "wiki") %>%
  filter(period <= 4)
wiki_seq_day5 <- sequences %>% 
  filter(type == "wiki") %>%
  filter(period <= 5)
wiki_seq_day6 <- sequences %>%
  filter(type == "wiki") %>%
  filter(period <= 6)
wiki_seq_day7 <- sequences %>%
  filter(type == "wiki") %>%
  filter(period <= 7)
wiki_seq_day8 <- sequences %>%
  filter(type == "wiki") %>%
  filter(period <= 8)
wiki_seq_day9 <- sequences %>%
  filter(type == "wiki") %>%
  filter(period <= 9)
wiki_seq_day10 <- sequences %>%
  filter(type == "wiki") %>%
  filter(period <= 10)
wiki_seq_day11 <- sequences %>%
  filter(type == "wiki") %>%
  filter(period <= 11)
wiki_seq_day12 <- sequences %>%
  filter(type == "wiki") %>%
  filter(period <= 12)
wiki_seq_day13 <- sequences %>%
  filter(type == "wiki") %>%
  filter(period <= 13)
wiki_seq_day14 <- sequences %>%
  filter(type == "wiki") %>%
  filter(period <= 14)
```


```{r}

wiki_activity_counts_day1 <- calculateActivityCount(wiki_seq_day1) %>% 
  addConditions()
wiki_activity_counts_day2 <- calculateActivityCount(wiki_seq_day2) %>% 
  addConditions()
wiki_activity_counts_day3 <- calculateActivityCount(wiki_seq_day3) %>% 
  addConditions()
wiki_activity_counts_day4 <- calculateActivityCount(wiki_seq_day4) %>% 
  addConditions()
wiki_activity_counts_day5 <- calculateActivityCount(wiki_seq_day5) %>% 
  addConditions()
wiki_activity_counts_day6 <- calculateActivityCount(wiki_seq_day6) %>% 
  addConditions()
wiki_activity_counts_day7 <- calculateActivityCount(wiki_seq_day7) %>% 
  addConditions()
wiki_activity_counts_day8 <- calculateActivityCount(wiki_seq_day8) %>% 
  addConditions()
wiki_activity_counts_day9 <- calculateActivityCount(wiki_seq_day9) %>% 
  addConditions()
wiki_activity_counts_day10 <- calculateActivityCount(wiki_seq_day10) %>% 
  addConditions()
wiki_activity_counts_day11 <- calculateActivityCount(wiki_seq_day11) %>% 
  addConditions()
wiki_activity_counts_day12 <- calculateActivityCount(wiki_seq_day12) %>% 
  addConditions()
wiki_activity_counts_day13 <- calculateActivityCount(wiki_seq_day13) %>% 
  addConditions()
wiki_activity_counts_day14 <- calculateActivityCount(wiki_seq_day14) %>% 
  addConditions()

changing_wiki_activity_count <- NULL

if (nrow(wiki_activity_counts_day1) > 0) {
  changing_wiki_activity_count <- wiki_activity_counts_day1
  changing_wiki_activity_count$period = 1
} else if (nrow(wiki_activity_counts_day2) > 0) {
  changing_wiki_activity_count <- wiki_activity_counts_day2
  changing_wiki_activity_count$period = 2
} else if (nrow(wiki_activity_counts_day3) > 0) {
  changing_wiki_activity_count <- wiki_activity_counts_day3
  changing_wiki_activity_count$period = 3
}


if (nrow(wiki_activity_counts_day1) > 0) {
  changing_wiki_activity_count <- addValues(changing_wiki_activity_count, wiki_activity_counts_day2, 2)
}

if (nrow(wiki_activity_counts_day1) == 0 && nrow(wiki_activity_counts_day2) > 0) {
  changing_wiki_activity_count <- addValues(changing_wiki_activity_count, wiki_activity_counts_day3, 3)
  changing_wiki_activity_count <- addValues(changing_wiki_activity_count, wiki_activity_counts_day4, 4)
}

if ((nrow(wiki_activity_counts_day1) == 0) && (nrow(wiki_activity_counts_day2) == 0) && (nrow(wiki_activity_counts_day3) > 0)) {
  changing_wiki_activity_count <- addValues(changing_wiki_activity_count, wiki_activity_counts_day4, 4)
}



changing_wiki_activity_count <- addValues(changing_wiki_activity_count, wiki_activity_counts_day5, 5)
changing_wiki_activity_count <- addValues(changing_wiki_activity_count, wiki_activity_counts_day6, 6)
changing_wiki_activity_count <- addValues(changing_wiki_activity_count, wiki_activity_counts_day7, 7)
changing_wiki_activity_count <- addValues(changing_wiki_activity_count, wiki_activity_counts_day8, 8)
changing_wiki_activity_count <- addValues(changing_wiki_activity_count, wiki_activity_counts_day9, 9)
changing_wiki_activity_count <- addValues(changing_wiki_activity_count, wiki_activity_counts_day10, 10)
changing_wiki_activity_count <- addValues(changing_wiki_activity_count, wiki_activity_counts_day11, 11)
changing_wiki_activity_count <- addValues(changing_wiki_activity_count, wiki_activity_counts_day12, 12)
changing_wiki_activity_count <- addValues(changing_wiki_activity_count, wiki_activity_counts_day13, 13)
changing_wiki_activity_count <- addValues(changing_wiki_activity_count, wiki_activity_counts_day14, 14)

write.csv2(changing_wiki_activity_count, "/home/doberstein/Dropbox/D/uni/IKARion/CVK MOOC - WS18_19/analysis/task1_changing_wiki_activity_count.csv")

```

## WIKI ACTIVITY DISTRIBUTION OVER DAYS BY CONDITION
<span style="color:blue">little activity in week one</span>
<span style="color:blue">more activities in groups with condition in the end</span>
```{r}
wiki_activity_distribution_for_condition <- changing_wiki_activity_count %>% 
  group_by(period) %>% 
  group_by(condition, add = T) %>% 
  summarise(accum_wiki_activity_count = sum(activity_count))
```

```{r}
ggplot(wiki_activity_distribution_for_condition, aes(x=period, y=accum_wiki_activity_count, group=condition)) +
  geom_line(aes(color=condition))+
  geom_point(aes(color=condition))+
  scale_x_continuous(labels = days, breaks = c(1:14))

```

## CLOSTER LOOK AT END OF GROUPTASK
```{r}

```

